---
title: "Analyses - Community Composition and Structural Equation Modelling"
output: html_document
date: "2026-01-20"
---

# Load Packages
```{r, message=FALSE}
library("tidyverse")
library("lme4")
library("lmerTest")
library("vegan")
library("corrplot")
library("Hmisc")
library("brms")
library("tidybayes")
library("ggpubr")
```

# Read in the Data
```{r, warning=FALSE}
#Clear environment
rm(list = ls())

setwd("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research")

#all site data
sites <- read.csv("data/sites_all.csv")
```

Making needed variables
```{r}
sites <- sites %>%
    mutate(water_wetland_1000m = water1000m + wetland1000m,
           n.enemy = n.pred + n.omn,
           species_per_m2 = flor.rich/floral_area_m2)
```


GGplot Theme
```{r}
Asia_Theme <- theme(
  plot.title = element_text(size = 16),
  plot.caption = element_text(size = 16),
  axis.title = element_text(size = 18),
  axis.text = element_text(size = 16),
  axis.text.x = element_text(size = 20),
  legend.text = element_text(size= 20))
```

# Habitat Quality and Environmental Variables

## Landscape Level Variables

Landscape Level Correlations
```{r}
#Landscape variables
site.landscape.input <- sites %>% select(-c(Site,site_code)) %>%
    select(WealthIndex, tcc200m, imp200m, tcc500m,imp500m,water1000m, wetland1000m, shrub_grass1000m)

#Landscape correlation test
landscape.rcorr = rcorr(as.matrix(site.landscape.input))
landscape.pvals <- landscape.rcorr$P

#Correlation plot
landscape.cor.plot <- corrplot(landscape.rcorr$r)
```

## Wealth and Landscape Variables Relationships
```{r}
#GBIF Landscape floral richness
wealth.land.plot1 <- ggplot(sites, aes(x = WealthIndex, y = gbif.rich))+
    geom_point()+
    geom_smooth()+
    ylab("Landscape floral richness (1 km)")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.land.plot1

#Tree canopy cover
wealth.land.plot2 <- ggplot(sites, aes(x = WealthIndex, y = tcc500m))+
    geom_point()+
    geom_smooth()+
    ylab("Tree Canopy Cover (500 m)")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.land.plot2

#Shrubland Cover
wealth.land.plot3 <- ggplot(sites, aes(x = WealthIndex, y = shrub_grass1000m))+
    geom_point()+
    geom_smooth()+
    ylab("Shrub & Grassland (1 km)")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.land.plot3

#Wetland Cover
wealth.land.plot4 <- ggplot(sites, aes(x = WealthIndex, y = water_wetland_1000m))+
    geom_point()+
    geom_smooth()+
    ylab("Water and Wetland (1 km)")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.land.plot4
```

## Wealth and Local Variables Relationships
```{r}
#Garden floral richness
wealth.loc.plot1 <- ggplot(sites, aes(x = WealthIndex, y = flor.simpson))+
    geom_point()+
    geom_smooth()+
    ylab("Garden floral richness")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.loc.plot1

#Garden Tree and Shrub Cover
wealth.loc.plot2 <- ggplot(sites, aes(x = WealthIndex, y = wood_m2))+
    geom_point()+
    geom_smooth()+
    ylab("Garden Tree and Shrub Cover")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.loc.plot2

#Garden Bareground Cover
wealth.loc.plot3 <- ggplot(sites, aes(x = WealthIndex, y = bareground_m2))+
    geom_point()+
    geom_smooth()+
    ylab("Garden Bareground Cover")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.loc.plot3

#Garden Bareground Cover
wealth.loc.plot4 <- ggplot(sites, aes(x = WealthIndex, y = species_per_m2))+
    geom_point()+
    geom_smooth()+
    ylab("Garden Floral Species/m2")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.loc.plot4
```
# Arthropod Abundance

Data Distributions
```{r}
#Total arthropod data
arth.hist <- ggplot(sites, aes(x = n.obs))+
    geom_histogram()+
    xlab("arthropod abundance")+
    theme_minimal()+
    Asia_Theme
arth.hist

pol.hist <- ggplot(sites, aes(x = n.pol))+
    geom_histogram()+
    xlab("pollinator abundance")+
    theme_minimal()+
    Asia_Theme
pol.hist
```
## Analysis

*What is the relationship between impervious surface, wealth, and total arthropod abundance?*
```{r}
set.seed(1)
arthropods_brms <- brms::brm(n.obs ~ imp200m + WealthIndex + month + (1|site_code),
                         data = sites, 
                         family = negbinomial(link = "log"), 
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)

summary(arthropods_brms)
plot(arthropods_brms)
loo(arthropods_brms,arthropods2_brms, compare = TRUE)
```

*What is the relationship between impervious surface, wealth, and pollinator, herbivore, and natural enemy abundances?*
```{r}
set.seed(1)
pol_brms <- brms::brm(n.pol ~ imp200m + WealthIndex + month + (1|site_code),
                         data = sites, 
                         family = negbinomial(link = "log"), 
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)


herb_brms <- brms::brm(n.herb ~ imp200m + WealthIndex + month + (1|site_code),
                         data = sites, 
                         family = negbinomial(link = "log"), 
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)
summary(herb_brms)

enemy_brms <- brms::brm(n.enemy ~ imp200m + WealthIndex + month + (1|site_code),
                         data = sites, 
                         family = negbinomial(link = "log"), 
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)
summary(pol_brms)
summary(herb_brms)
summary(enemy_brms)
#plot(pol_brms)
```


## Plots

Making site variables prediction grid
```{r}
sitevar.pred <- tidyr::expand_grid(
  imp200m = seq(min(sites$imp200m), max(sites$imp200m), length.out = 100),
  site_code = unique(sites$site_code),
  month = unique(sites$month),
  WealthIndex = mean(sites$WealthIndex, na.rm = TRUE))
```

#### Total Arthropod Abundance & Landscape Variables 
```{r, message=FALSE}
#Generate predictions on grid from arthropod brms model
arth.preds  <- sitevar.pred  %>%
  add_epred_draws(arthropods_brms, ndraws = 200)

#Total arthropod abundance and Impervious Surface with brms estimate with credible intervals
arth.imp.plot <- ggplot(arth.preds, aes(x = imp200m, y = .epred)) +
  stat_lineribbon(.width = c(.95, .80, .50),
                  alpha = 0.5, colour = "black") +
  geom_point(data = sites,
             aes(x = imp200m, y = n.obs),
             colour = "darkseagreen4", size = 3) +
  scale_fill_brewer(palette = "Greys") +
  ylab("Total arthropod abundance") +
  xlab("Impervious surface 200 m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
arth.imp.plot 

#Total arthropod abundance and Wealth Index with brms estimate with credible intervals
arth.wealth.plot <- ggplot(arth.preds, aes(x = WealthIndex, y = .epred)) +
  stat_lineribbon(.width = c(.95, .80, .50),
                  alpha = 0.5, colour = "black") +
  geom_point(data = sites,
             aes(x = WealthIndex, y = n.obs),
             colour = "darkseagreen4", size = 3) +
  scale_fill_brewer(palette = "Greys") +
  ylab("Total arthropod abundance") +
  xlab("Wealth Index 500 m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
arth.wealth.plot 

arthropods.panelplot <- ggarrange(arth.imp.plot, arth.wealth.plot, ncol = 2, labels = "AUTO")
```
### Pollinator Abundance and Landscape Variables
```{r, message=FALSE}
#Generate predictions on grid from pollinator brms model
pol.preds  <- sitevar.pred  %>%
  add_epred_draws(pol_brms, ndraws = 300)

#Pollinator abundance and Impervious Surface
pol.imp.plot <- ggplot(pol.preds, aes(x = imp200m, y = .epred, color = month)) +
  geom_smooth() +
  geom_point(data = sites,
             aes(x = imp200m, y = n.pol), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
  ylab("Pollinator abundance") +
  xlab("Impervious surface 200 m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
pol.imp.plot

#Pollinator abundance and Wealth Index
pol.wealth.plot <- ggplot(pol.preds, aes(x = WealthIndex, y = .epred, color = month)) +
  geom_smooth() +
  geom_point(data = sites,
             aes(x = WealthIndex, y = n.pol), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
  ylab("Pollinator abundance") +
  xlab("Wealth Index 500 m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
pol.wealth.plot 
```

### Herbivore Abundance and Landscape Variables
```{r}
#Generate predictions on grid from herbivore brms model
herb.preds  <- sitevar.pred  %>%
  add_epred_draws(herb_brms, ndraws = 300)

#Herbivore abundance and Impervious Surface
herb.imp.plot <- ggplot(herb.preds, aes(x = imp200m, y = .epred, color = month)) +
  geom_smooth() +
  geom_point(data = sites,
             aes(x = imp200m, y = n.herb), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
  ylab("Herbivore abundance") +
  xlab("Impervious surface 200 m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
herb.imp.plot

#Herbivore abundance and Wealth Index
herb.wealth.plot <- ggplot(herb.preds, aes(x = WealthIndex, y = .epred,  color = month)) +
  geom_smooth() +
  geom_point(data = sites,
             aes(x = WealthIndex, y = n.herb), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
  ylab("Herbivore abundance") +
  xlab("Wealth Index 500 m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
herb.wealth.plot 
```

### Natural Enemy Abundance and Landscape Variables
```{r}
#Generate predictions on grid from herbivore brms model
enemy.preds  <- sitevar.pred  %>%
  add_epred_draws(enemy_brms, ndraws = 300)

#Natural Enemy abundance and Impervious Surface
enemy.imp.plot <- ggplot(enemy.preds, aes(x = imp200m, y = .epred, color = month)) +
  geom_smooth() +
  geom_point(data = sites,
             aes(x = imp200m, y = n.enemy), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
  ylab("Natural Enemy abundance") +
  xlab("Impervious surface 200 m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
enemy.imp.plot

#Herbivore abundance and Wealth Index
enemy.wealth.plot <- ggplot(enemy.preds, aes(x = WealthIndex, y = .epred,  color = month)) +
  geom_smooth() +
  geom_point(data = sites,
             aes(x = WealthIndex, y = n.enemy), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
  ylab("Natural Enemy abundance") +
  xlab("Wealth Index 500 m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
enemy.wealth.plot 
```
Panel plot for all functional groups
```{r}
fungroup.panelplot <- ggarrange(pol.imp.plot, pol.wealth.plot, herb.imp.plot, herb.wealth.plot, enemy.imp.plot, enemy.wealth.plot, 
        ncol = 2, nrow = 3, 
        labels = "AUTO",
        common.legend = TRUE)
```

## Bee Species Richness
```{r}
#Bee richness and Impervious Surface
bee.imp.plot <- ggplot(sites, aes(x = imp200m, y = bee.rich))+
    geom_point()+
    facet_wrap(vars(month), ncol = 3)+
    ylab("Bee richness")+
    xlab("Impervious surface (200 m)")+
    theme_minimal()+
    Asia_Theme
bee.imp.plot

#Bee richness and Wealth Index
bee.wealth.plot <- ggplot(sites, aes(x = WealthIndex, y = bee.rich))+
    geom_point()+
    facet_wrap(vars(month), ncol = 3)+
    ylab("Bee richness")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
bee.wealth.plot
```
# Cucumber Outcomes

## Analysis

```{r}

```

## Plots

### Cucumbers and Bee Richness
```{r}
cuc.beerich.plot1 <- ggplot(sites, aes(x = bee.rich, y = delta_seed_mass_ratio))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beerich.plot1 

cuc.beerich.plot2 <- ggplot(sites, aes(x = bee.rich, y = delta_no))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beerich.plot2 

cuc.beerich.plot3 <- ggplot(sites, aes(x = bee.rich, y = delta_cylindrical))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beerich.plot3 

cuc.beerich.plot4 <- ggplot(sites, aes(x = bee.rich, y = delta_volume))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beerich.plot4
```

### Cucumbers and Bee Shannon Diversity
```{r}
cuc.beeshan.plot1 <- ggplot(sites, aes(x = bee.shannon, y = delta_seed_mass_ratio))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beeshan.plot1 

cuc.beeshan.plot2 <- ggplot(sites, aes(x = bee.shannon, y = delta_no))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beeshan.plot2 

cuc.beeshan.plot3 <- ggplot(sites, aes(x = bee.shannon, y = delta_cylindrical))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beeshan.plot3 

cuc.beeshan.plot4 <- ggplot(sites, aes(x = bee.shannon, y = delta_volume))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beeshan.plot4
```


# Habitat Quality Index
```{r}

```

# Structural Equation Modelling
```{r}

```

# Save Images
```{r}
ggsave("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/figures/Arthropods_PanelFig.pdf", plot = arthropods.panelplot, height = 7, width = 10)

ggsave("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/figures/FunctionalGroups_PanelFig.pdf", plot = fungroup.panelplot, height = 11, width = 7)
```

