---
title: "Analyses - Community Composition and Structural Equation Modelling"
output: html_document
date: "2026-01-20"
---

# Load Packages
```{r, message=FALSE}
library("tidyverse")
library("lme4")
library("lmerTest")
library("vegan")
library("corrplot")
library("Hmisc")
```

# Read in the Data
```{r, warning=FALSE}
#Clear environment
rm(list = ls())

setwd("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research")

#all site data
sites <- read.csv("data/sites_all.csv")

#matrix data for community analyses
inat_wide <- read.csv("data/inat_wide.csv")
arthropods_wide <- read.csv("data/arthropods_wide.csv")
```

# Explore the Data
```{r}

```

GGplot Theme
```{r}
Asia_Theme <- theme(
  plot.title = element_text(size = 16),
  plot.caption = element_text(size = 16),
  axis.title = element_text(size = 20),
  axis.text = element_text(size = 16),
  axis.text.x = element_text(size = 20),
  legend.text = element_text(size= 20))
```

# Habitat Quality and Environmental Variables

Select variables of interest
```{r}
#Aggregated values across months
site_cov <- sites %>%
    filter(month == "June")%>%
    select(Site, site_code, Area_m2, Plots, WealthIndex, tcc200m, imp200m, tcc500m,imp500m,CWD_m2,wood_m2,FWD_m2,logs,bareground_m2,floral_area_m2,dev_high500m, dev_low500m,wetland500m, water500m,	dev_high1000m, dev_low1000m, water1000m, wetland1000m, shrub_grass1000m)
```

## Landscape Level Variables

Landscape Correlations
```{r}
site.landscape.input <- site_cov %>% select(-c(Site,site_code)) %>%
    select(WealthIndex, tcc200m, imp200m, tcc500m,imp500m,water1000m, wetland1000m, shrub_grass1000m)
```

Landscape Correlation Plot
```{r}
#Test for significant correlations
landscape.rcorr = rcorr(as.matrix(site.landscape.input))
landscape.pvals <- landscape.rcorr$P



landscape.cor.plot <- corrplot(landscape.rcorr$r)
```

# Arthropod Data Full Summer
```{r}
site_cov <- sites %>%
    filter(month == "June")%>%
    select(c("site_code","tcc200m","imp200m","tcc500m","imp500m","WealthIndex","floral_area_m2","flor.rich"))
```

# Community Composition
## Floral NMDS
```{r, echo=FALSE}
set.seed(10)
florNMDS_input <- inat_wide[,-1]
florNMDS_input <- florNMDS_input[, colSums(florNMDS_input > 0) >= 5]

flor.mds <- metaMDS(florNMDS_input, k = 2, trymax = 20)
flor.mds

#Make nmds into dataframe for plotting
flor.mds.scores <- as.data.frame(scores(flor.mds, display = "sites"))
flor.mds.scores <- cbind(flor.mds.scores, site_cov)
```

Floral Community NMDS Plot
```{r}
flor.mds.plot <- 
    ggplot(flor.mds.scores, aes(x = NMDS1, y = NMDS2)) +
  geom_point(aes(color = WealthIndex), size = 3) +
  theme_minimal() +
  labs(
    title = "NMDS Ordination of Floral Genera",
    x = "NMDS1",
    y = "NMDS2",
    color = "[Env Covariate]"
  ) +
  coord_fixed()
flor.mds.plot
```

## Arthropod Functional Groups
```{r, echo=FALSE}
set.seed(100)
arthropodsNMDS_input <- arthropods_wide[,-1]
arthropodsNMDS_input <- arthropodsNMDS_input[, colSums(arthropodsNMDS_input > 0) >= 30] # remove uncommon taxa to reduce stress
arthropodsNMDS_input <- arthropodsNMDS_input %>% select(-Unknown)

arthropods.mds <- metaMDS(arthropodsNMDS_input, trymax = 50)
arthropods.mds

#make nmds into dataframe for plotting
arthropods.mds.scores <- as.data.frame(scores(arthropods.mds, display = "sites"))
arthropods_columns <- arthropods_wide %>%
    separate(site_month, into = c("site", "month"), sep = "_")%>%
    select(site,month)%>%
    mutate(site_code = site)

arthropods.mds.scores$site_code <- arthropods_columns$site_code
arthropods.mds.scores$month <- arthropods_columns$month
arthropods.mds.scores <-left_join(arthropods.mds.scores, site_cov, by = "site_code")
```

Arthropod Functional Groups NMDS Plot
```{r}
arthropods.mds.plot <- 
    ggplot(arthropods.mds.scores, aes(x = NMDS1, y = NMDS2)) +
  geom_point(aes(color = imp200m), size = 3) +
  theme_minimal() +
  labs(
    title = "NMDS Ordination of Arthropod Functional Groups",
    x = "NMDS1",
    y = "NMDS2",
    color = "[Env Covariate]"
  ) +
  coord_fixed()
arthropods.mds.plot
```

## Bee Species NMDS
```{r}

```

# Habitat Quality Index
```{r}

```

# Structural Equation Modelling
```{r}

```

