---
title: "Analyses - Community Composition and Structural Equation Modelling"
output: html_document
date: "2026-01-20"
---

# Load Packages

```{r, message=FALSE}
library("tidyverse")
library("lme4")
library("lmerTest")
library("vegan")
library("corrplot")
library("Hmisc")
library("brms")
library("tidybayes")
library("ggpubr")
library("mgcv")
library("loo")
library("cmdstanr")
library("rstan")
library("mgcv")
library("modelsummary")
library("performance")
library("broom.mixed")
library("marginaleffects") 
```

# Read in the Data

```{r, warning=FALSE}
#Clear environment
rm(list = ls())

#all site data
sites <- read.csv("../data/sites_all.csv")
```

Making needed variables

```{r}
sites <- sites %>%
    mutate(water_wetland_1000m = water_1000m + wetland_1000m,
           n.enemy = n.pred + n.omn,
           species_per_m2 = inat.rich/floral_area_m2,
           imp200m_s = as.numeric(scale(imp_200m)),
           imp500m_s = as.numeric(scale(imp_500m)),
           WealthIndex_s = as.numeric(scale(WealthIndex)),
           WI_high = pmax(WealthIndex - 140, 0),
           WI_high_s = as.numeric(scale(WI_high)))

#keep month as a factor
sites$month <- as.factor(sites$month)
```

GGplot Theme

```{r}
Asia_Theme <- theme(
  plot.title = element_text(size = 16),
  plot.caption = element_text(size = 16),
  axis.title = element_text(size = 18),
  axis.text = element_text(size = 16),
  axis.text.x = element_text(size = 20),
  legend.text = element_text(size= 20))
```

# Arthropod Abundance

Data Distributions

```{r}
#histograms of the abundance of all arthropods, pollinators, herbivores, and predators
arthropod.vars <- c("n.obs", "n.pol", "n.herb", "n.enemy")

for(var in arthropod.vars) {
  plot <- ggplot(sites, aes(x = .data[[var]])) +
    geom_histogram() +
    labs(x = var) +
    theme_minimal() +
    Asia_Theme

  print(plot)
}
```

## Analysis

*What is the relationship between impervious surface, wealth, and total arthropod abundance?*

```{r}
set.seed(10)
#Setting priors
priors_arth <- c(
  prior(normal(log(80), 0.5), class = "Intercept"),
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sd"),
  prior(gamma(2, 0.1), class = "shape"))

arthropods_brms <- brms::brm(
  formula = n.obs ~ imp200m_s + WealthIndex_s + month + (1 | site_code),
  data = sites, 
  family = negbinomial(link = "log"),
  prior = priors_arth,
  chains = 4,
  mc.cores = parallel::detectCores(), 
  iter = 2500,
  warmup = 1000,
  backend = "cmdstanr",
  file = "../analyses/brms_models/arthropods_brms") #saves model to disk

summary(arthropods_brms)

#posterior predictive check
brms::pp_check(arthropods_brms, ndraws = 50)
```

Running model again at the 500meter scale and doing leave one out cross validation to compare model fit and confirm best spatial scale

```{r}
set.seed(10)
# Run the 500m model
arthropods_brms_500m <- brms::brm(
  formula = n.obs ~ imp500m_s + WealthIndex_s + month + (1 | site_code),
  data = sites, 
  family = negbinomial(link = "log"),
  prior = priors_arth,
  chains = 4, mc.cores = parallel::detectCores(), iter = 2500, warmup = 1000,
  backend = "cmdstanr", 
  file = "../analyses/brms_models/arthropod_brms_500m")

# Compute LOO for both models
arthropods_brms      <- add_criterion(arthropods_brms, criterion = "loo")
arthropods_brms_500m <- add_criterion(arthropods_brms_500m, criterion = "loo")

# Compare the models
model_comparison <- loo_compare(arthropods_brms, arthropods_brms_500m)
print(model_comparison, simplify = FALSE)
```

*What is the relationship between impervious surface, wealth, and pollinator, herbivore, and natural enemy abundances?*

```{r}
#Test for non-linear response to wealth in pollinators
gam_fit <- gam(n.pol ~ s(WealthIndex_s) + imp200m_s + month,
               data = sites,
               family = nb())
summary(gam_fit) #no significant non-linear relationship with wealth
plot(gam_fit, pages = 1)

#SETTING PRIORS
priors_pol <- c(
  prior(normal(log(10), 0.5), class = "Intercept"),
  prior(normal(0, 0.5), class = "b"),
  prior(exponential(1), class = "sd"),
  prior(gamma(2, 0.1), class = "shape")
)

priors_herb <- c(
  prior(normal(log(20), 0.5), class = "Intercept"),
  prior(normal(0, 0.5), class = "b"),
  prior(exponential(1), class = "sd"),
  prior(gamma(2, 0.1), class = "shape")
)

priors_enemy <- c(
  prior(normal(log(18), 0.4), class = "Intercept"),
  # Slightly tighter regularization for potentially noisier predator responses
  prior(normal(0, 0.4), class = "b"),
  prior(exponential(1), class = "sd"),
  prior(gamma(2, 0.1), class = "shape")
)


set.seed(100)

#POLLINATORS
pol_brms <- brms::brm(
  formula = n.pol ~ imp200m_s + WealthIndex_s + month + (1 | site_code),
  data = sites, 
  family = negbinomial(link = "log"),
  prior = priors_pol,
  chains = 4, mc.cores = parallel::detectCores(), iter = 2500, warmup = 1000,
  backend = "cmdstanr", 
  file = "../analyses/brms_models/pol_brms"
)

#HERBIVORES
herb_brms <- brms::brm(
  formula = n.herb ~ imp200m_s + WealthIndex_s + month + (1 | site_code),
  data = sites, 
  family = negbinomial(link = "log"),
  prior = priors_herb,
  chains = 4, mc.cores = parallel::detectCores(), iter = 2500, warmup = 1000,
  backend = "cmdstanr", 
  file = "../analyses/brms_models/herb_brms"
)

#NATURAL ENEMIES (Predators, Parasitoids)
enemy_brms <- brms::brm(
  formula = n.enemy ~ imp200m_s + WealthIndex_s + month + (1 | site_code),
  data = sites, 
  family = negbinomial(link = "log"),
  prior = priors_enemy,
  chains = 4, cores = 4, iter = 2500, warmup = 1000,
    control = list(
    adapt_delta = 0.99,
    max_treedepth = 15),
  backend = "cmdstanr", 
  file = "../analyses/brms_models/enemy_brms"
)

summary(pol_brms)
summary(herb_brms)
summary(enemy_brms)

#posterior predictive checks
brms::pp_check(pol_brms, ndraws = 50)
brms::pp_check(herb_brms, ndraws = 50)
brms::pp_check(enemy_brms, ndraws = 50)
#plot(pol_brms)
```

## Plots

Making site variables prediction grid

```{r}
wealth_ref <- mean(sites$WealthIndex, na.rm = TRUE)
imp_ref <- mean(sites$imp_200m, na.rm = TRUE)

imp_center <- mean(sites$imp_200m, na.rm = TRUE)
imp_scale  <- sd(sites$imp_200m, na.rm = TRUE)

wealth_center <- mean(sites$WealthIndex, na.rm = TRUE)
wealth_scale  <- sd(sites$WealthIndex, na.rm = TRUE)

# Prediction grid for impervious surface
sitevar.pred.imp <- tidyr::expand_grid(
  imp_200m = seq(
    min(sites$imp_200m, na.rm = TRUE),
    max(sites$imp_200m, na.rm = TRUE),
    length.out = 50
  ),
  site_code = unique(sites$site_code),
  month = unique(sites$month)
) %>%
  mutate(
    WealthIndex = wealth_ref,
    imp200m_s = (imp_200m - imp_center) / imp_scale,
    WealthIndex_s = (WealthIndex - wealth_center) / wealth_scale
  )
```

#### Total Arthropod Abundance & Landscape Variables

```{r, message=FALSE}
#Generate predictions on grid from arthropod brms model
arth.preds.imp <- sitevar.pred.imp %>%
  add_epred_draws(arthropods_brms, ndraws = 200)

#Total arthropod abundance and Impervious Surface with brms estimate with credible intervals
arth.imp.plot <- ggplot(arth.preds.imp, aes(x = imp_200m, y = .epred)) +
  stat_lineribbon(.width = c(.95, .80, .50),
                  alpha = 0.5, colour = "black") +
  geom_point(data = sites,
             aes(x = imp_200m, y = n.obs),
             colour = "darkseagreen4", size = 3) +
  scale_fill_brewer(palette = "Greys") +
  ylab("Total arthropod abundance") +
  xlab("Impervious surface 200m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
arth.imp.plot 

#Total arthropod abundance and Wealth Inde
arth.wealth.plot <- ggplot(arth.preds.imp, aes(x = WealthIndex, y = .epred)) +
  geom_point(data = sites,
             aes(x = WealthIndex, y = n.obs),
             colour = "darkseagreen4", size = 3) +
  scale_fill_brewer(palette = "Greys") +
  ylab("Total arthropod abundance") +
  xlab("Wealth Index 500m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
arth.wealth.plot 

#Effect size plot with credible intervals

## Extract the model estimates and 95% Credible Intervals
effect_arthropods <- tidy(arthropods_brms, effects = "fixed", conf.int = TRUE, conf.level = 0.95) %>%
  filter(term %in% c("imp200m_s", "WealthIndex_s")) %>%
  mutate(term = recode(term, 
                       "imp200m_s" = "Impervious surface", 
                       "WealthIndex_s" = "Wealth Index"))

effect.plot.arthropods <- ggplot(effect_arthropods, aes(x = term, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_linerange(aes(ymin = conf.low, ymax = conf.high), linewidth = 1, 
                 color = c("darkseagreen4", "gray")) +
  geom_point(size = 3,
             color = c("darkseagreen4", "gray")) +
  ylab("Beta estimate") +
  xlab(NULL) +
  theme_minimal() +
  Asia_Theme
effect.plot.arthropods 

arthropods.panelplot <- ggarrange(arth.imp.plot, arth.wealth.plot, ncol = 2, labels = "AUTO")
```

### Pollinator Abundance and Landscape Variables

```{r, message=FALSE}
#Generate predictions on grid from pollinator brms model
pol.preds.imp <- sitevar.pred.imp %>%
  add_epred_draws(pol_brms, ndraws = 200)

#Pollinator abundance and Impervious Surface
pol.imp.plot <- ggplot(pol.preds.imp, aes(x = imp_200m, y = .epred, color = month)) +
  geom_smooth()+
  geom_point(data = sites,
             aes(x = imp_200m, y = n.pol, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
     scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Pollinator abundance") +
  xlab("Impervious surface 200m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
pol.imp.plot

#Pollinator abundance and Wealth Index
pol.wealth.plot <- ggplot(pol.preds.imp, aes(x = WealthIndex, y = .epred, color = month)) +
  geom_point(data = sites,
             aes(x = WealthIndex, y = n.pol, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
     scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Pollinator abundance") +
  xlab("Wealth Index 500m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
pol.wealth.plot

#Effect size plot with credible intervals
effect_pol <- tidy(pol_brms, effects = "fixed", conf.int = TRUE, conf.level = 0.95) %>%
  filter(term %in% c("imp200m_s", "WealthIndex_s")) %>%
  mutate(term = recode(term, 
                       "imp200m_s" = "Impervious surface", 
                       "WealthIndex_s" = "Wealth Index"))

effect.plot.pol <- ggplot(effect_pol, aes(x = term, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_linerange(aes(ymin = conf.low, ymax = conf.high), linewidth = 1, 
                 color = c("darkseagreen4", "gray")) +
  geom_point(size = 3,
             color = c("darkseagreen4", "gray")) +
  ylab("Beta estimate") +
  xlab(NULL) +
  theme_minimal() +
  Asia_Theme
effect.plot.pol 
```

### Herbivore Abundance and Landscape Variables

```{r}
#Generate predictions on grid from herbivore brms model
herb.preds.imp <- sitevar.pred.imp %>%
  add_epred_draws(herb_brms, ndraws = 200)

#Herbivore abundance and Impervious Surface
herb.imp.plot <- ggplot(herb.preds.imp, aes(x = imp_200m, y = .epred, color = month)) +
  geom_smooth() +
  geom_point(data = sites,
             aes(x = imp_200m, y = n.herb, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
    scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Herbivore abundance") +
  xlab("Impervious surface 200m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
herb.imp.plot

#Herbivore abundance and Wealth Index
herb.wealth.plot <- ggplot(herb.preds.imp, aes(x = WealthIndex, y = .epred,  color = month)) +
  geom_point(data = sites,
             aes(x = WealthIndex, y = n.herb, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
    scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Herbivore abundance") +
  xlab("Wealth Index 500m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
herb.wealth.plot 

#effect size with credible intervals
effect_herb <- tidy(herb_brms, effects = "fixed", conf.int = TRUE, conf.level = 0.95) %>%
  filter(term %in% c("imp200m_s", "WealthIndex_s")) %>%
  mutate(term = recode(term, 
                       "imp200m_s" = "Impervious surface", 
                       "WealthIndex_s" = "Wealth Index"))

effect.plot.herb <- ggplot(effect_herb, aes(x = term, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_linerange(aes(ymin = conf.low, ymax = conf.high), linewidth = 1, 
                 color = c("darkseagreen4", "gray")) +
  geom_point(size = 3,
             color = c("darkseagreen4", "gray")) +
  ylab("Beta estimate") +
  xlab(NULL) +
  theme_minimal() +
  Asia_Theme
effect.plot.herb 
```

### Natural Enemy Abundance and Landscape Variables

```{r}
#Generate predictions on grid from natural enemy brms model
enemy.preds.imp <- sitevar.pred.imp %>%
  add_epred_draws(enemy_brms, ndraws = 200)

#Natural Enemy abundance and Impervious Surface
enemy.imp.plot <- ggplot(enemy.preds.imp, aes(x = imp_200m, y = .epred, color = month)) +
  geom_smooth() +
  geom_point(data = sites,
             aes(x = imp_200m, y = n.enemy, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
    scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Natural Enemy abundance") +
  xlab("Impervious surface 200m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
enemy.imp.plot

#Natural enemy abundance and Wealth Index
enemy.wealth.plot <- ggplot(enemy.preds.imp, aes(x = WealthIndex, y = .epred,  color = month)) +
  geom_point(data = sites,
             aes(x = WealthIndex, y = n.enemy, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
    scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Natural Enemy abundance") +
  xlab("Wealth Index 500m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
enemy.wealth.plot 

#effect sizes with credible intervals
effect_enemy <- tidy(enemy_brms, effects = "fixed", conf.int = TRUE, conf.level = 0.95) %>%
  filter(term %in% c("imp200m_s", "WealthIndex_s")) %>%
  mutate(term = recode(term, 
                       "imp200m_s" = "Impervious surface", 
                       "WealthIndex_s" = "Wealth Index"))

effect.plot.enemy <- ggplot(effect_enemy, aes(x = term, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_linerange(aes(ymin = conf.low, ymax = conf.high), linewidth = 1, 
                 color = c("darkseagreen4", "gray")) +
  geom_point(size = 3,
             color = c("darkseagreen4", "gray")) +
  ylab("Beta estimate") +
  xlab(NULL) +
  theme_minimal() +
  Asia_Theme
effect.plot.enemy 
```

## Bee Species Richness

Data distributions
```{r}
#filtering sites to June because data was aggregated across the summer for bee richness
sites_june <- sites %>% filter(month == "June")

bee.vars <- c("bee.rich", "bee.shannon", "bee.simpson")

for(var in bee.vars) {
  plot <- ggplot(sites_june, aes(x = .data[[var]])) +
    geom_histogram() +
    labs(x = var) +
    theme_minimal() +
    Asia_Theme
  print(plot)
}
```


```{r}
#Exploratory Test for non-linear response to wealth in bees
library(mgcv)
sites$site_code <- as.factor(sites$site_code)

gam_fit_re <- gam(
  bee.rich ~ s(WealthIndex_s) + imp200m_s + month + 
    s(site_code, bs = "re"),
  data = sites,
  family = poisson()
)
summary(gam_fit_re) #non-linear!
plot(gam_fit, pages = 1)


set.seed(10)

#SETTING PRIORS
priors_bee_rich <- c(
  prior(normal(1.38, 0.5), class = "Intercept"),
  prior(normal(0, 0.25), class = "b"),
  prior(normal(0, 0.5), class = "sds", coef = "s(WealthIndex_s)"),
  prior(exponential(2), class = "sd", group = "site_code")
)

priors_bee_shannon <- c(
  prior(normal(1.25, 0.5), class = "Intercept"),
  prior(normal(0, 0.25), class = "b"),
  prior(exponential(1), class = "sigma"),
  prior(normal(0, 0.5), class = "sds", coef = "s(WealthIndex_s)"),
  prior(exponential(2), class = "sd", group = "site_code")
)

priors_bee_simpson <- c(
  prior(normal(1.10, 0.5), class = "Intercept"),
  prior(normal(0, 0.25), class = "b"),
  prior(exponential(1), class = "sigma"),
  prior(normal(0, 0.5), class = "sds", coef = "s(WealthIndex_s)"),
  prior(exponential(2), class = "sd", group = "site_code")
)

#MODELLING BEE RICHNESS
bees_brms <- brms::brm(
  formula = bee.rich ~ s(WealthIndex_s) + imp200m_s + month + (1|site_code),
  data = sites, 
  family = poisson(link = "log"), 
  prior = priors_bee_rich, 
  chains = 4, 
  cores = 4, 
  iter = 3000,
  warmup = 1500,
  control = list(
    adapt_delta = 0.99,
    max_treedepth = 15),
  backend = "cmdstanr", 
  file = "../analyses/brms_models/bees_brms_gam",
)

#MODELLING BEE SHANNON DIVERSITY
shannon_brms <- brms::brm(
  formula = bee.shannon ~ imp200m_s + s(WealthIndex_s) + month + (1|site_code),
  data = sites, 
  family = lognormal(link = "identity"),
  prior = priors_bee_shannon,         
  chains = 4, cores = 4, iter = 3500, warmup = 2000,
  control = list(
    adapt_delta = 0.99,
    max_treedepth = 15),
  backend = "cmdstanr", 
  file = "../analyses/brms_models/shannon_brms"
)

#MODELLING BEE SIMPSON DIVERSITY
simpson_brms <- brms::brm(
  formula = bee.simpson ~ imp200m_s + s(WealthIndex_s) + month + (1|site_code),
  data = sites, 
  family = lognormal(link = "identity"), 
  prior = priors_bee_simpson,         
  chains = 4, cores = 4, iter = 2500, warmup = 1000,
  control = list(
    adapt_delta = 0.99,
    max_treedepth = 15),
  backend = "cmdstanr", 
  file = "../analyses/brms_models/simpson_brms",
)

summary(bees_brms)
pp_check(bees_brms,ndraws = 50)
rich_eff <- conditional_effects(bees_brms, effects = "WealthIndex_s")

summary(shannon_brms)
pp_check(shannon_brms,ndraws = 50)
shannon_eff <-conditional_effects(shannon_brms, effects = "WealthIndex_s")

summary(simpson_brms)
pp_check(simpson_brms,ndraws = 50)
simpson_eff <-conditional_effects(simpson_brms, effects = "WealthIndex_s")

sites$bee.shannon
```

Posterior estimates of Wealth Index peak for bee diversity metrics
```{r}
# 0. Define raw scale constants
raw_mean <- mean(sites$WealthIndex, na.rm = TRUE)
raw_sd   <- sd(sites$WealthIndex, na.rm = TRUE)

# 1. Set up the fine prediction grid
grid <- data.frame(
  WealthIndex_s = seq(
    min(sites$WealthIndex_s, na.rm = TRUE),
    max(sites$WealthIndex_s, na.rm = TRUE),
    length.out = 500
  ),
  imp200m_s = 0,
  month = levels(sites$month)[1]
)

# 2. Store your models in a named list
models <- list(
  "Bee Richness"      = bees_brms,
  "Shannon Diversity" = shannon_brms,
  "Simpson Diversity" = simpson_brms
)

# 3. Extract peak per posterior draw for each model
peaks_per_draw <- map_dfr(models, function(mod) {
  add_epred_draws(grid, mod, re_formula = NA) %>%
    group_by(.draw) %>%
    slice_max(.epred, n = 1, with_ties = FALSE) %>%
    ungroup()
}, .id = "metric") %>%
  mutate(WealthIndex_raw = (WealthIndex_s * raw_sd) + raw_mean)

# 4. Summarize median peaks and 95% Credible Intervals for all 3 metrics
peak_summary_all <- peaks_per_draw %>%
  group_by(metric) %>%
  median_qi(WealthIndex_raw, WealthIndex_s, .width = 0.95)

# View the combined summary table
print(peak_summary_all)

ggplot(peaks_per_draw, aes(x = WealthIndex_raw, y = metric, fill = metric)) +
  stat_halfeye(.width = c(0.66, 0.95), alpha = 0.8) +
  labs(
    x = "Wealth Index (Raw Peak Location)",
    y = NULL,
    title = "Posterior Peak Locations for Bee Metrics"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```


Bee Plots
- Plot and focus on shannon diversity perhaps for full story (impervious surface, conditional  effects, cucumbers)
```{r}
# --- GRID 1: IMPERVIOUS SURFACE PREDICTIONS ---
sitevar.pred.imp <- expand_grid(
  imp_200m = seq(min(sites$imp_200m, na.rm = TRUE), max(sites$imp_200m, na.rm = TRUE), length.out = 50),
  site_code = unique(sites$site_code),
  month = unique(sites$month)) %>%
  mutate(
    imp200m_s = (imp_200m - imp_center) / imp_scale,
    WealthIndex_s = 0
  )

bees.preds.imp <- sitevar.pred.imp %>%
  add_epred_draws(shannon_brms, ndraws = 200)

#Impervious Surface
bees.imp.plot <- ggplot(bees.preds.imp, aes(x = imp_200m, y = .epred, color = month)) +
geom_smooth()+
  geom_point(data = sites,
             aes(x = imp_200m, y = bee.shannon, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
     scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  labs(y = "bee Shannon diversity", x = "Impervious surface 200m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85)) +
  Asia_Theme 

bees.imp.plot
```

Panel plot for all functional groups

```{r}
fungroup.panelplot <- ggarrange(pol.imp.plot, pol.wealth.plot, effect.plot.pol, herb.imp.plot, herb.wealth.plot, effect.plot.herb, enemy.imp.plot, enemy.wealth.plot,effect.plot.enemy,
        ncol = 3, nrow = 3, 
        labels = "AUTO",
        font.label = list(size = 25, face = "bold"),
        common.legend = TRUE)
```

# Cucumber Outcomes

Created dataset aggregated by summer

```{r}
#one full summer data set, summing arthropod values across months
sem_data <- sites%>%
    filter(!is.na(bee.shannon)) %>%
    group_by(site_code)%>%
    summarise(n.herb = sum(n.herb),
              n.pol = sum(n.pol),
              n.enemy = sum(n.enemy),
              n.pred = sum(n.pred),
              WealthIndex = mean(WealthIndex),
              tcc200m = mean(tcc_200m),
              tcc500m = mean(tcc_500m),
              tcc1000m = mean(tcc_1000m),
              imp200m = mean(imp_200m),
              imp500m = mean(imp_500m),
              wood_m2 = mean(wood_m2),
              bareground_m2 = mean(bareground_m2),
              floral_area_m2 = mean(floral_area_m2),
              shrub_grass1000m = mean(shrub_grass_1000m),
              gbif.rich = mean(gbif.rich),
              gbif.shannon = mean(gbif.shannon),
              gbif.simpson = mean(gbif.simpson),
              flor.rich = mean(inat.rich),
              flor.shannon = mean(inat.shannon),
              flor.simpson = mean(inat.simpson),
              delta_mass = mean(delta_mass),
              delta_cylindrical = mean(delta_cylindrical),
              delta_length = mean(delta_length),
              delta_width = mean(delta_width),
              delta_volume = mean(delta_volume),
              delta_seed_mass_ratio = mean(delta_seed_mass_ratio),
              delta_seeds = mean(delta_seeds),
              delta_no = mean(delta_no),
              n.obs = sum(n.obs),
              bee.rich = sum(bee.rich),
              bee.shannon = sum(bee.shannon),
              bee.simpson = sum(bee.simpson),
              water_wetland_1000m = mean(water_wetland_1000m),
              species_per_m2 = mean(species_per_m2),
              imp200m_s = mean(imp200m_s),
              WealthIndex_s = mean(WealthIndex_s),
              WI_high = mean(WI_high),
              WI_high_s = mean(WI_high_s)
    )%>%
    mutate(
        n.pol_s = as.numeric(scale(n.pol)),
        n.herb_s = as.numeric(scale(n.herb)),
        n.enemy_s = as.numeric(scale(n.enemy))
    )

sem_data

#Scaling bee shannon index and accounting for NA value

sem_data$bee.shannon_s <- (
  sem_data$bee.shannon - mean(sem_data$bee.shannon, na.rm = TRUE)
) / sd(sem_data$bee.shannon, na.rm = TRUE)

sem_data$bee.shannon_s

sem_data$bee.rich_s <- (
  sem_data$bee.rich - mean(sem_data$bee.rich, na.rm = TRUE)
) / sd(sem_data$bee.rich, na.rm = TRUE)

sem_data$bee.rich_s
```

Explore cucumber outcome data for normality

```{r}
c_outcomes <- c("delta_seeds", "delta_mass", "delta_cylindrical", "delta_no", "delta_length", "delta_width", "delta_volume") 

for (i in c_outcomes) {
  print(i)
  hist(sem_data[[i]],
       main = paste("Histogram of", i),
       xlab = i)
}
```

Regressions looking at each arthropod group and cucumber outcomes
```{r}
priors_no <- c(
    #Cucumber Abundance
  prior(normal(0, 2), class = "b"),
  prior(normal(0, 5), class = "Intercept"),
  prior(exponential(0.2), class = "sigma"),
  prior(gamma(2, 0.1), class = "nu")
)

priors_seeds <- c(
    #Seed Count
  prior(normal(0, 10), class = "b"),
  prior(normal(0, 40), class = "Intercept"),
  prior(exponential(0.03), class = "sigma"),
  prior(gamma(2, 0.1), class = "nu")
)

priors_mass <- c(
    #Fruit mass
  prior(normal(0, 20), class = "b"),
  prior(normal(0, 75), class = "Intercept"),
  prior(exponential(0.02), class = "sigma"),
  prior(gamma(2, 0.1), class = "nu")
)

priors_cylindrical <- c(
    #Cylindricity 
  prior(normal(0, 0.2), class = "b"),
  prior(normal(0, 0.5), class = "Intercept"),
  prior(exponential(4), class = "sigma")
)


abundance_cuc_brms <- brms::brm(delta_no ~ bee.shannon_s + n.pol_s + n.herb_s + n.enemy_s,  family = student(), 
                      data = sem_data,
                      prior = priors_no,
                      chains = 4,
                      cores = 4, 
                      iter = 2500,
                      warmup = 1000,
                      backend = "cmdstanr",
                      file = "../analyses/brms_models/abundance_cuc_brms",
                      file_refit = "on_change")

seeds_cuc_brms <- brms::brm(delta_seeds ~ bee.shannon_s + n.pol_s + n.herb_s + n.enemy_s,  family = student(), 
                      data = sem_data,
                      prior = priors_seeds,
                      chains = 3, cores = 4, iter = 2500, warmup = 1000,
                      backend = "cmdstanr",
                      file = "../analyses/brms_models/seeds_cuc_brms",
                      file_refit = "on_change")

mass_cuc_brms <- brms::brm(delta_mass ~ bee.shannon_s + n.pol_s + n.herb_s + n.enemy_s,  family = student(), 
                      data = sem_data,
                      prior = priors_mass,
                      chains = 3, cores = 4, iter = 2500, warmup = 1000,
                      backend = "cmdstanr",
                      file = "../analyses/brms_models/mass_cuc_brms",
                      file_refit = "on_change")

cylindrical_cuc_brms <- brms::brm(delta_cylindrical ~ bee.shannon_s + n.pol_s + n.herb_s + n.enemy_s,  family = gaussian(), 
                      data = sem_data,
                      prior = priors_cylindrical,
                      chains = 3, cores = 4, iter = 2500, warmup = 1000,
                      backend = "cmdstanr",
                      file = "../analyses/brms_models/cylindrical_cuc_brms",
                      file_refit = "on_change")

summary(abundance_cuc_brms)
summary(seeds_cuc_brms)
summary(mass_cuc_brms)
summary(cylindrical_cuc_brms)
```
Abundance and Shannon diversity are the only relevant variables. Look at their distributions to create priors for sem
```{r}
hist(sem_data$bee.shannon_s)
hist(sem_data$delta_no)
```

## Structural Equation Modelling

Put arthropod mediator models in correct format
```{r}
bf_pol   <- bf(n.pol ~ imp200m_s + WealthIndex_s, family = negbinomial())
bf_herb  <- bf(n.herb ~ imp200m_s + WealthIndex_s, family = negbinomial())
bf_enemy <- bf(n.enemy ~ imp200m_s + WealthIndex_s, family = negbinomial())

#Add quadratic estimator (spline too computationally expensive) to Wealth Index for bee data for non-linear effect

#bf_bee   <- bf(bee.shannon_s ~ imp200m_s + WealthIndex_s + I(WealthIndex_s^2), family = gaussian())

bf_bee   <- bf(bee.shannon_s ~ imp200m_s + s(WealthIndex_s), family = gaussian())
bf_cuc   <- bf(delta_no ~ bee.shannon_s, family = student())
```

Setting global priors

```{r}
priors_full_sem <- c(
  # Arthropods
  prior(normal(0, 0.5), class = "b", resp = "npol"),
  prior(normal(0, 0.5), class = "b", resp = "nherb"),
  prior(normal(0, 0.5), class = "b", resp = "nenemy"),

  prior(normal(1, 1.5), class = "Intercept", resp = "npol"),
  prior(normal(1, 1.5), class = "Intercept", resp = "nherb"),
  prior(normal(1, 1.5), class = "Intercept", resp = "nenemy"),

  prior(exponential(1), class = "shape", resp = "npol"),
  prior(exponential(1), class = "shape", resp = "nherb"),
  prior(exponential(1), class = "shape", resp = "nenemy"),

  # Bee Shannon
  prior(normal(0, 0.5), class = "b", resp = "beeshannons"),
  prior(normal(0, 1), class = "Intercept", resp = "beeshannons"),
  prior(exponential(1), class = "sigma", resp = "beeshannons"),

  # Cucumber
  prior(normal(0, 0.5), class = "b", resp = "deltano"),
  prior(normal(0, 1), class = "Intercept", resp = "deltano"),
  prior(exponential(1), class = "sigma", resp = "deltano"),
  prior(gamma(2, 0.1), class = "nu", resp = "deltano")
)
#Ended up not keeping a full SEM, too computationally expensive

priors_sem <- c(
  # Bee Shannon
  prior(normal(0, 0.5), class = "Intercept", resp = "beeshannons"),
  prior(normal(0, 0.5), class = "b", resp = "beeshannons"),
  prior(exponential(2), class = "sigma", resp = "beeshannons"),
  prior(normal(0, 0.5), class = "sds", coef = "s(WealthIndex_s)", resp = "beeshannons"),
  
  #Cucumber abundance
  prior(normal(0, 5), class = "Intercept", resp = "deltano"), 
  prior(normal(0, 2), class = "b", resp = "deltano"),
  prior(exponential(0.2), class = "sigma", resp = "deltano"),
  prior(gamma(2, 0.1), class = "nu", resp = "deltano")
)
#More modest SEM keeping just relevant predictors
```

Structural Equation Model

```{r}
set.seed(100)

fit_sem <- brm(
  bf_bee + bf_cuc + set_rescor(FALSE),
  data = sem_data,
  prior = priors_sem,
  chains = 4,
  cores = 4, 
  iter = 2500,
  warmup = 1000,
  control = list(adapt_delta = 0.99, max_treedepth = 15),
  backend = "cmdstanr",
  file = "../analyses/brms_models/fit_sem",
  file_refit = "on_change"
)

summary(fit_sem)
mcmc_plot(fit_sem, variable = "^b_", regex = TRUE, type = "intervals") +
  theme_minimal() +
  labs(title = "Posterior Intervals for SEM Path Coefficients",
       x = "Estimate Scale")

pp_deltano <- pp_check(fit_sem, resp = "deltano", ndraws = 50) +
  theme_classic() +
  theme(plot.title = element_text(size = 12))+
  labs(title = "Cucumber Abundance",
       x = "Observed vs. Simulated Values")

pp_shannon <- pp_check(fit_sem, resp = "beeshannons", ndraws = 50) +
  theme_classic() +
  theme(plot.title = element_text(size = 12))+
  labs(title = "Bee Shannon Diversity",
       x = "Observed vs. Simulated Values")

pplot_sem <- ggarrange(pp_deltano, pp_shannon,
  ncol = 2,
  common.legend = TRUE,
  legend = "bottom")

#Measuirng indrect effects
draws <- as_draws_df(fit_sem) #posterior draws for the path coefficients

draws <- draws %>%
  mutate(indirect_imp_cucumber = b_beeshannons_imp200m_s* b_deltano_bee.shannon_s) # Indirect Effect = Path A * Path B

median_qi(draws$indirect_imp_cucumber, .width = 0.95)
```

## Plots

### Cucumbers and Bee Richness

```{r}
cuc.beerich.plot1 <- ggplot(sem_data, aes(x = bee.rich, y = delta_seeds))+
    geom_point()+
    geom_smooth(method = "lm", se = FALSE, linetype = "dashed")+
    xlab("Bee Richness")+
    ylab("seed ct.")+
    theme_classic()+
    Asia_Theme
cuc.beerich.plot1 

cuc.beerich.plot2 <- ggplot(sem_data, aes(x = bee.rich, y = delta_no))+
    geom_point()+
    geom_smooth(method = "lm", se = FALSE, linetype = "dashed")+
    ylab("abundance")+
    xlab("Bee Richness")+
    theme_classic()+
    Asia_Theme
cuc.beerich.plot2 

cuc.beerich.plot3 <- ggplot(sem_data, aes(x = bee.rich, y = delta_cylindrical))+
    geom_point()+
    geom_smooth(method = "lm", se = FALSE, linetype = "dashed")+
    ylab("prop. cylindrical")+
    xlab("Bee Richness")+
    theme_classic()+
    Asia_Theme
cuc.beerich.plot3 

cuc.beerich.plot4 <- ggplot(sem_data, aes(x = bee.rich, y = delta_mass))+
    geom_point()+
    geom_smooth(method = "lm", se = FALSE, linetype = "dashed")+
    ylab("fruit mass")+
    xlab("Bee Richness")+
    theme_classic()+
    Asia_Theme
cuc.beerich.plot4
```

### Cucumbers and Bee Shannon Diversity

```{r}
cuc.beeshan.plot1 <- ggplot(sem_data, aes(x = bee.shannon, y = delta_seeds))+
    geom_point()+
    geom_smooth(method = "lm", se = FALSE, linetype = "dashed")+
    ylab("seed ct.")+
    xlab("Shannon diversity")+
    theme_classic()+
    Asia_Theme
cuc.beeshan.plot1 

cuc.beeshan.plot2 <- ggplot(sem_data, aes(x = bee.shannon , y = delta_no))+
    geom_point()+
    geom_smooth(method = "lm", se = TRUE)+
    ylab("abundance")+
    xlab("Shannon diversity")+
    theme_classic()+
    Asia_Theme
cuc.beeshan.plot2 

cuc.beeshan.plot3 <- ggplot(sem_data, aes(x = bee.shannon, y = delta_cylindrical))+
    geom_point()+
    geom_smooth(method = "lm", se = FALSE, linetype = "dashed")+
    ylab("prop. cylindrical")+
    xlab("Shannon diversity")+
    theme_classic()+
    Asia_Theme
cuc.beeshan.plot3 

cuc.beeshan.plot4 <- ggplot(sem_data, aes(x = bee.shannon, y = delta_mass))+
    geom_point()+
    geom_smooth(method = "lm", se = FALSE, linetype = "dashed")+
    ylab("fruit mass")+
    xlab("Shannon diversity")+
    theme_classic()+
    Asia_Theme
cuc.beeshan.plot4
```

### Cucumbers and Pollinator Abundance

```{r}
cuc.pol.plot1 <- ggplot(sem_data, aes(x = n.pol, y = delta_seeds))+
    geom_point()+
    geom_smooth(method = "lm", se = FALSE, linetype = "dashed")+
    ylab("seed ct.")+
    xlab("pollinators")+
    theme_classic()+
    Asia_Theme
cuc.pol.plot1 

cuc.pol.plot2 <- ggplot(sem_data, aes(x =n.pol, y = delta_no))+
    geom_point()+
    geom_smooth(method = "lm", se = FALSE, linetype = "dashed")+
    ylab("abundance")+
    xlab("pollinators")+
    theme_classic()+
    Asia_Theme
cuc.pol.plot2 

cuc.pol.plot3 <- ggplot(sem_data, aes(x = n.pol, y = delta_cylindrical))+
    geom_point()+
    geom_smooth(method = "lm", se = FALSE, linetype = "dashed")+
    ylab("prop. cylindrical")+
    xlab("pollinators")+
    theme_classic()+
    Asia_Theme
cuc.pol.plot3 

cuc.pol.plot4 <- ggplot(sem_data, aes(x = n.pol, y = delta_mass))+
    geom_point()+
    geom_smooth(method = "lm", se = FALSE, linetype = "dashed")+
    xlab("pollinators")+
    ylab("fruit mass")+
    theme_classic()+
    Asia_Theme
cuc.pol.plot4
```

Combined cucumber outcome plot for supplements

```{r}
cucumber.panelplot <- ggarrange(cuc.beerich.plot1,cuc.beeshan.plot1,cuc.pol.plot1, cuc.beerich.plot2, cuc.beeshan.plot2, cuc.pol.plot2, cuc.beerich.plot3, cuc.beeshan.plot3, cuc.pol.plot3, cuc.beerich.plot4, cuc.beeshan.plot4, cuc.pol.plot4,
        ncol = 3, nrow = 4,
        common.legend = TRUE)
```

Bee shannon diversity and no of cucumbers plot
```{r}
cuc_brms <- brms::brm(delta_no ~ bee.shannon,  family = student(), 
                      data = sem_data,
                      prior = priors_cuc,
                    chains = 3, cores = 4, iter = 2000, warmup = 1000,
                    backend = "cmdstanr",
  file = "../analyses/brms_models/cuc_brms_plot")
```

```{r}
#Generate predictions on grid from brms model
pred_grid <- tibble(
  bee.shannon = seq(
    min(sem_data$bee.shannon, na.rm = TRUE),
    max(sem_data$bee.shannon, na.rm = TRUE),
    length.out = 100
  )
)

cuc.preds <- pred_grid %>%
  add_epred_draws(cuc_brms, ndraws = 200)


#Cucumbers and bee shannon diversity with brms estimate with credible intervals
cuc.plot <- ggplot(cuc.preds, aes(x = bee.shannon, y = .epred)) +
  stat_lineribbon(.width = c(.95, .80, .50),
                  alpha = 0.5, colour = "black") +
  geom_point(data = sem_data,
             aes(x = bee.shannon, y = delta_no),
             colour = "darkseagreen4", size = 3) +
  scale_fill_brewer(palette = "Greys") +
  ylab(expression(atop(Delta ~ "cucumber abundance", "(open - hand pollinated)")))+
  xlab("bee Shannon diversity") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.15))+
    Asia_Theme
cuc.plot 
```
Combine all shannon diversity plots
```{r}
#Create a plot in my style for conditional effects
#RICHNESS
rich.wealth.plot <- plot(rich_eff, plot = FALSE)$WealthIndex_s +
  labs(
    x = "Scaled Wealth Index",
    y = "bee richness"
  ) +
  theme_minimal() +
  Asia_Theme
rich.wealth.plot

#SHANNON
shannon.wealth.plot <- plot(shannon_eff, plot = FALSE)$WealthIndex_s +
  labs(
    x = "Scaled Wealth Index",
    y = "bee Shannon diversity"
  ) +
  theme_minimal() +
  Asia_Theme
shannon.wealth.plot

#SIMPSON
simpson.wealth.plot <- plot(simpson_eff, plot = FALSE)$WealthIndex_s +
  labs(
    x = "Scaled Wealth Index",
    y = "bee Simpson diversity"
  ) +
  theme_minimal() +
  Asia_Theme
simpson.wealth.plot

cond.effects.plot <- ggarrange(rich.wealth.plot, shannon.wealth.plot, simpson.wealth.plot, ncol = 3, labels = "AUTO",common.legend = TRUE)
bees.panelplot <- ggarrange(bees.imp.plot, shannon.wealth.plot, cuc.plot, ncol = 3, labels = "AUTO",common.legend = TRUE)
```

# Habitat Quality

Look at the relationship between local and landscape variable and wealth index

### Local variables
```{r}
set.seed(1)
hist(sem_data$wood_m2)
hist(sem_data$bareground_m2)
hist(sem_data$flor.rich)
hist(sem_data$flor.shannon)
hist(sem_data$species_per_m2)

#WOODY (Tree and Shrub Cover)
wood_brms <- brm(
  bf(wood_m2 ~ WealthIndex_s,
     hu ~ 1),
  family = hurdle_gamma(link = "log"),
  prior = c(
    prior(normal(0, 1), class = "b"),
    prior(normal(4, 1.5), class = "Intercept"),
    prior(normal(0, 1.5), class = "Intercept", dpar = "hu"),
    prior(gamma(2, 0.5), class = "shape")
  ),
  data = sem_data,
  chains = 4, cores = 4, iter = 2500, warmup = 1000,
  backend = "cmdstanr",
  file = "../analyses/brms_models/wood_brms",
  file_refit = "on_change"
)

#BAREGROUND
bare_brms <- brm(
  bf(bareground_m2 ~ WealthIndex_s,
     hu ~ 1),
  family = hurdle_gamma(link = "log"),
  prior = c(
    prior(normal(0, 1), class = "b"),
    prior(normal(2.5, 1.5), class = "Intercept"),
    prior(normal(0, 1.5), class = "Intercept", dpar = "hu"),
    prior(gamma(2, 0.5), class = "shape")
  ),
  data = sem_data,
  chains = 4, cores = 4, iter = 2500, warmup = 1000,
  backend = "cmdstanr",
  file = "../analyses/brms_models/bare_brms",
  file_refit = "on_change"
)

#FLORAL RICHNESS
# Gaussian: Data spans ~20 to 110 (SD looks to be around 15-20)
flor_rich_brms <- brm(
  flor.rich ~ WealthIndex_s,
  family = gaussian(),
  prior = c(
    prior(normal(60, 15), class = "Intercept"),
    prior(normal(0, 5), class = "b"),
    prior(exponential(0.05), class = "sigma")
  ),
  data = sem_data,
  chains = 4, cores = 4, iter = 2500, warmup = 1000,
  backend = "cmdstanr",
  file = "../analyses/brms_models/flor_rich_brms",
  file_refit = "on_change"
)

#FLORAL DIVERSITY
# Gaussian: Data spans ~10 to 80 (SD around 10-15)
flor_shannon_brms <- brm(
  flor.shannon ~ WealthIndex_s,
  family = gaussian(),
  prior = c(
    prior(normal(45, 15), class = "Intercept"),
    prior(normal(0, 5), class = "b"),
    prior(exponential(0.08), class = "sigma")
  ),
  data = sem_data,
  chains = 4, cores = 4, iter = 2500, warmup = 1000,
  backend = "cmdstanr",
  file = "../analyses/brms_models/flor_shannon_brms",
  file_refit = "on_change"
)

#FLORAL DENSITY
flor_density_brms <- brm(
  species_per_m2 ~ WealthIndex_s,
  family = lognormal(),
  prior = c(
    prior(normal(-1, 1), class = "Intercept"),
    prior(normal(0, 1), class = "b"),
    prior(exponential(2), class = "sigma")
  ),
  data = sem_data,
  chains = 4, cores = 4, iter = 2500, warmup = 1000,
  backend = "cmdstanr",
  file = "../analyses/brms_models/flor_density_brms",
  file_refit = "on_change"
)

summary(wood_brms)
summary(flor_rich_brms)
summary(flor_shannon_brms)
summary(bare_brms)
summary(flor_density_brms)
```

### Landscape variables
```{r}
set.seed(1)
hist(sem_data$tcc500m)
hist(sem_data$water_wetland_1000m)
hist(sem_data$gbif.rich)
hist(sem_data$gbif.shannon)
hist(sem_data$shrub_grass1000m)

#testing correlation between wealth index and impervious surface
cor.test(sem_data$imp500m, sem_data$WealthIndex)

#TREE CANOPY COVER
tcc_brms <- brm(
  tcc500m ~ WealthIndex_s, 
  family = gaussian(),  
  prior = c(
    prior(normal(0, 5), class = "b"),  
    prior(normal(12, 5), class = "Intercept"),
    prior(exponential(0.1), class = "sigma")
  ),
  data = sem_data,
  chains = 4, cores = 4, iter = 2500, warmup = 1000,
  backend = "cmdstanr",
  file = "../analyses/brms_models/tcc_brms",
  file_refit = "on_change"
)

#WATER WETLAND
waterwet_brms <- brm(
  bf(water_wetland_1000m ~ WealthIndex_s, 
     hu ~ 1),
  family = hurdle_gamma(link = "log"),
  prior = c(
    prior(normal(-3.2, 0.5), class = "Intercept"),
    prior(normal(0, 1), class = "b"),
    prior(normal(0, 1.5), class = "Intercept", dpar = "hu"),
    prior(gamma(10, 2), class = "shape")          
  ),
  data = sem_data, chains = 4, cores = 4, iter = 2500, warmup = 1000,
  backend = "cmdstanr", file = "../analyses/brms_models/waterwet_brms",
  file_refit = "on_change"
)

#GBIF EST. RICHNESS
gbifrich_brms <- brm(
  gbif.rich ~ WealthIndex_s,
  family = gaussian(),
  prior = c(
    prior(normal(115, 30), class = "Intercept"),
    prior(normal(0, 20), class = "b"),
    prior(exponential(0.03), class = "sigma")
  ),
  data = sem_data, chains = 4, cores = 4, iter = 2500, warmup = 1000,
  backend = "cmdstanr", file = "../analyses/brms_models/gbifrich_brms",
  file_refit = "on_change"
)

#GBIF EST. SHANNON DIVERSITY
gbifshannon_brms <- brm(
  gbif.shannon ~ WealthIndex_s,
  family = gaussian(),
  prior = c(
    prior(normal(80, 25), class = "Intercept"),
    prior(normal(0, 15), class = "b"),
    prior(exponential(0.04), class = "sigma")
  ),
  data = sem_data, chains = 4, cores = 4, iter = 2500, warmup = 1000,
  backend = "cmdstanr", file = "../analyses/brms_models/gbifshannon_brms",
  file_refit = "on_change"
)

#SHRUB & GRASSLAND
shrubgrass_brms <- brm(
  bf(shrub_grass1000m ~ WealthIndex_s, 
     hu ~ 1),
  family = hurdle_gamma(link = "log"),
  prior = c(
    prior(normal(-3.9, 0.5), class = "Intercept"),
    prior(normal(0, 1), class = "b"),
    prior(normal(0, 1.5), class = "Intercept", dpar = "hu"),
    prior(gamma(10, 2), class = "shape")          
  ),
  data = sem_data, chains = 4, cores = 4, iter = 2500, warmup = 1000,
  backend = "cmdstanr", file = "../analyses/brms_models/shrubgrass_brms",
  file_refit = "on_change"
)


summary(tcc_brms)
summary(gbifrich_brms)
summary(gbifshannon_brms)
summary(waterwet_brms)
summary(shrubgrass_brms)
```

# Export Model Summary Outputs
```{r}
modelsummary(
  list("total arthropod abundance" = arthropods_brms,
       "pollinator abundance" = pol_brms,
       "herbivore abundance" = herb_brms,
       "natural enemy abundance" = enemy_brms,
       "bee richness" = bees_brms,
       "bee shannon" = shannon_brms,
       "bee simpson" = simpson_brms,
       "cucumber sem" = fit_sem,
       "cucumer abundance" = abundance_cuc_brms,
       "seed count" = seeds_cuc_brms,
       "fruit mass" = mass_cuc_brms,
       "cylindricity" = cylindrical_cuc_brms
       ), 
  statistic = "conf.int", 
  metrics = c("BIC", "R2")
)

brms_models <- list("total arthropod abundance" = arthropods_brms,
       "pollinator abundance" = pol_brms,
       "herbivore abundance" = herb_brms,
       "natural enemy abundance" = enemy_brms,
       "bee richness" = bees_brms,
       "bee shannon" = shannon_brms,
       "bee simpson" = simpson_brms,
       "cucumer abundance" = abundance_cuc_brms,
       "seed count" = seeds_cuc_brms,
       "fruit mass" = mass_cuc_brms,
       "cylindricity" = cylindrical_cuc_brms
       )

for (model in brms_models) {
  tidy_summary <- tidy(
  model, 
  effects = c("fixed", "ran_pars"),
  conf.int = TRUE,
  conf.level = 0.95,
  robust = FALSE) 
  
  print(tidy_summary)
}

tidy_summary <- tidy(
  fit_sem, 
  effects = c("fixed", "ran_pars"),
  conf.int = TRUE,
  conf.level = 0.95,
  robust = FALSE) 
  
  print(tidy_summary)
```


## Posterior Plots

Arthropod Models
```{r}
brms_arthropods <- list("total arthropod abundance" = arthropods_brms,
       "pollinator abundance" = pol_brms,
       "herbivore abundance" = herb_brms,
       "natural enemy abundance" = enemy_brms,
       "bee richness" = bees_brms,
       "bee shannon" = shannon_brms,
       "bee simpson" = simpson_brms
       )

plot_list <- list()
for (model_name in names(brms_arthropods)) {
  current_model <- brms_arthropods[[model_name]]
  
  #posterior plot
  p <- brms::pp_check(current_model, ndraws = 50) +
    labs(title = model_name) +
    theme(plot.title = element_text(size = 10))
  plot_list[[model_name]] <- p
}

post.plots.arthropods <- do.call(ggarrange, c(
  plot_list, 
  ncol = 3,
  nrow = 3,
  common.legend = TRUE,
  legend = "bottom"
))

print(post.plots.arthropods)
```

Cucumber Models
```{r}
brms_cuc <- list(
       "cucumer abundance" = abundance_cuc_brms,
       "seed count" = seeds_cuc_brms,
       "fruit mass" = mass_cuc_brms,
       "cylindricity" = cylindrical_cuc_brms
       )

plot_list <- list()
for (model_name in names(brms_cuc)) {
  current_model <- brms_cuc[[model_name]]
  
  #posterior plot
  p <- brms::pp_check(current_model, ndraws = 50) +
    labs(title = model_name) +
    theme(plot.title = element_text(size = 10))
  plot_list[[model_name]] <- p
}

post.plots.cuc <- do.call(ggarrange, c(
  plot_list, 
  ncol = 2, 
  nrow = 2,
  common.legend = TRUE,
  legend = "bottom"
))

print(post.plots.cuc)
```

Local Habitat Models
```{r}
brms_loc <- list(
       "Tree & shrub cover" = wood_brms,
       "Floral richness" = flor_rich_brms,
       "Floral Shannon diversity" = flor_shannon_brms,
       "Bareground" = bare_brms,
       "Floral density" = flor_density_brms
       )

plot_list <- list()
for (model_name in names(brms_loc)) {
  current_model <- brms_loc[[model_name]]
  
  #posterior plot
  p <- brms::pp_check(current_model, ndraws = 50) +
    labs(title = model_name) +
    theme(plot.title = element_text(size = 10))
  plot_list[[model_name]] <- p
}

post.plots.loc <- do.call(ggarrange, c(
  plot_list, 
  ncol = 3, 
  nrow = 2,
  common.legend = TRUE,
  legend = "bottom"
))

print(post.plots.loc)

for (model in brms_loc) {
  tidy_summary <- tidy(
  model, 
  effects = c("fixed", "ran_pars"),
  conf.int = TRUE,
  conf.level = 0.95,
  robust = FALSE) 
    
  print(tidy_summary)
}
```

Landscape Habitat Models
```{r}
brms_land <- list(
       "Tree canopy cover" = tcc_brms,
       "Est. floral richness" = gbifrich_brms,
       "Est. floral Shannon diversity" = gbifshannon_brms,
       "Water & wetland" = waterwet_brms,
       "Shrub & grassland" = shrubgrass_brms
       )

plot_list <- list()
for (model_name in names(brms_land)) {
  current_model <- brms_land[[model_name]]
  
  #posterior plot
  p <- brms::pp_check(current_model, ndraws = 50) +
    labs(title = model_name) +
    theme(plot.title = element_text(size = 10))
  plot_list[[model_name]] <- p
}

post.plots.land <- do.call(ggarrange, c(
  plot_list, 
  ncol = 3, 
  nrow = 2,
  common.legend = TRUE,
  legend = "bottom"
))

print(post.plots.land)

for (model in brms_land) {
  tidy_summary <- tidy(
  model, 
  effects = c("fixed", "ran_pars"),
  conf.int = TRUE,
  conf.level = 0.95,
  robust = FALSE) 
    
  print(tidy_summary)
}
```

# Save Images

```{r}
set.seed(100)

ggsave("../figures/Arthropods_PanelFig.pdf", plot = arthropods.panelplot, height = 6, width = 10)

ggsave("../figures/Bees_PanelFig.pdf", plot = bees.panelplot, height = 5, width = 12)

ggsave("../figures/FunctionalGroups_PanelFig.pdf", plot = fungroup.panelplot, height = 12, width = 12)

ggsave("../figures/Cucumber_plot.pdf", plot = cuc.plot, height = 6, width = 6)

ggsave("../figures/Cucumbers_PanelFig.png", plot = cucumber.panelplot, height = 10, width = 10)

ggsave("../figures/Supp_ConditionalEffects.png", plot = cond.effects.plot, height = 5, width = 12)

ggsave("../figures/posterior_plots/Posteriors_Arthropods.png", plot = post.plots.arthropods)
ggsave("../figures/posterior_plots/Posteriors_Cucumbers.png", plot = post.plots.cuc)
ggsave("../figures/posterior_plots/Posteriors_LocalHabitat.png", plot = post.plots.loc)
ggsave("../figures/posterior_plots/Posteriors_LandscapeHabitat.png", plot = post.plots.land)
ggsave("../figures/posterior_plots/Posteriors_SEM.png", plot = pplot_sem, height = 3, width = 5)

```

# Session Info and Packages

```{r}
packageVersion("brms")
```
