---
title: "Analyses - Community Composition and Structural Equation Modelling"
output: html_document
date: "2026-01-20"
---

# Load Packages
```{r, message=FALSE}
library("tidyverse")
library("lme4")
library("lmerTest")
library("vegan")
library("corrplot")
library("Hmisc")
library("brms")
library("tidybayes")
library("ggpubr")
library("mgcv")
library("loo")
```

# Read in the Data
```{r, warning=FALSE}
#Clear environment
rm(list = ls())

setwd("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research")

#all site data
sites <- read.csv("data/sites_all.csv")
```

Making needed variables
```{r}
sites <- sites %>%
    mutate(water_wetland_1000m = water1000m + wetland1000m,
           n.enemy = n.pred + n.omn,
           species_per_m2 = flor.rich/floral_area_m2,
           imp200m_s = as.numeric(scale(imp200m)),
           WealthIndex_s = as.numeric(scale(WealthIndex)),
           WI_high = pmax(WealthIndex - 155, 0),
           WI_high_s = as.numeric(scale(WI_high)))

attributes(scale(sites$WealthIndex))
attributes(scale(sites$WI_high))
```


GGplot Theme
```{r}
Asia_Theme <- theme(
  plot.title = element_text(size = 16),
  plot.caption = element_text(size = 16),
  axis.title = element_text(size = 18),
  axis.text = element_text(size = 16),
  axis.text.x = element_text(size = 20),
  legend.text = element_text(size= 20))
```

# Habitat Quality and Environmental Variables

## Landscape Level Variables

Landscape Level Correlations
```{r}
#Landscape variables
site.landscape.input <- sites %>% select(-c(Site,site_code)) %>%
    select(WealthIndex, tcc200m, imp200m, tcc500m,imp500m,water1000m, wetland1000m, shrub_grass1000m)

#Landscape correlation test
landscape.rcorr = rcorr(as.matrix(site.landscape.input))
landscape.pvals <- landscape.rcorr$P

#Correlation plot
landscape.cor.plot <- corrplot(landscape.rcorr$r)
```

## Wealth and Landscape Variables Relationships
```{r}
#GBIF Landscape floral richness
wealth.land.plot1 <- ggplot(sites, aes(x = WealthIndex, y = gbif.rich))+
    geom_point()+
    geom_smooth()+
    ylab("Landscape floral richness (1 km)")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.land.plot1

#Tree canopy cover
wealth.land.plot2 <- ggplot(sites, aes(x = WealthIndex, y = tcc500m))+
    geom_point()+
    geom_smooth()+
    ylab("Tree Canopy Cover (500 m)")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.land.plot2

#Shrubland Cover
wealth.land.plot3 <- ggplot(sites, aes(x = WealthIndex, y = shrub_grass1000m))+
    geom_point()+
    geom_smooth()+
    ylab("Shrub & Grassland (1 km)")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.land.plot3

#Wetland Cover
wealth.land.plot4 <- ggplot(sites, aes(x = WealthIndex, y = water_wetland_1000m))+
    geom_point()+
    geom_smooth()+
    ylab("Water and Wetland (1 km)")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.land.plot4
```

## Wealth and Local Variables Relationships
```{r}
#Garden floral richness
wealth.loc.plot1 <- ggplot(sites, aes(x = WealthIndex, y = flor.simpson))+
    geom_point()+
    geom_smooth()+
    ylab("Garden floral richness")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.loc.plot1

#Garden Tree and Shrub Cover
wealth.loc.plot2 <- ggplot(sites, aes(x = WealthIndex, y = wood_m2))+
    geom_point()+
    geom_smooth()+
    ylab("Garden Tree and Shrub Cover")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.loc.plot2

#Garden Bareground Cover
wealth.loc.plot3 <- ggplot(sites, aes(x = WealthIndex, y = bareground_m2))+
    geom_point()+
    geom_smooth()+
    ylab("Garden Bareground Cover")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.loc.plot3

#Garden Bareground Cover
wealth.loc.plot4 <- ggplot(sites, aes(x = WealthIndex, y = species_per_m2))+
    geom_point()+
    geom_smooth()+
    ylab("Garden Floral Species/m2")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.loc.plot4
```
# Arthropod Abundance

Data Distributions
```{r}
#Total arthropod data
arth.hist <- ggplot(sites, aes(x = n.obs))+
    geom_histogram()+
    xlab("arthropod abundance")+
    theme_minimal()+
    Asia_Theme
arth.hist

pol.hist <- ggplot(sites, aes(x = n.pol))+
    geom_histogram()+
    xlab("pollinator abundance")+
    theme_minimal()+
    Asia_Theme
pol.hist

herb.hist <- ggplot(sites, aes(x = n.herb))+
    geom_histogram()+
    xlab("herbivore abundance")+
    theme_minimal()+
    Asia_Theme
herb.hist

pred.hist <- ggplot(sites, aes(x = n.pred))+
    geom_histogram()+
    xlab("predator abundance")+
    theme_minimal()+
    Asia_Theme
pred.hist
```
## Analysis

*What is the relationship between impervious surface, wealth, and total arthropod abundance?*
```{r}
set.seed(10)

#Setting priors
priors_arth <- c(
  prior(normal(log(80), 1.5), class = "Intercept"),
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sd"),
  prior(exponential(0.5), class = "shape")
)

arthropods_brms <- brms::brm(n.obs ~ imp200m_s + WealthIndex_s + month + (1|site_code),
                         data = sites, 
                         family = negbinomial(link = "log"),
                         prior = priors_arth,
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)

#plot(arthropods_brms)
#conditional_effects(arthropods_brms)
summary(arthropods_brms)
```

*What is the relationship between impervious surface, wealth, and pollinator, herbivore, and natural enemy abundances?*
```{r}
#Test for non-linear response to wealth in pollinators
gam_fit <- gam(n.pol ~ s(WealthIndex) + imp200m + month,
               data = sites,
               family = nb())
summary(gam_fit) #no significant non-linear relationship with wealth
plot(gam_fit, pages = 1)

priors_pol <- c(
  prior(normal(log(15), 2), class = "Intercept"),
  prior(normal(0, 1.5), class = "b"),
  prior(exponential(1), class = "sd"),
  prior(exponential(1), class = "shape")
)

priors_herb <- c(
  prior(normal(log(15), 1.5), class = "Intercept"),
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sd"),
  prior(exponential(1), class = "shape")
)

priors_enemy <- c(
  prior(normal(log(10), 1.5), class = "Intercept"),
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sd"),
  prior(exponential(1), class = "shape")
)

set.seed(100)
pol_brms <- brms::brm(n.pol ~ imp200m_s + WealthIndex_s + month + (1|site_code),
                      data = sites, 
                      family = negbinomial(link = "log"),
                      prior = priors_pol,
                      chains = 3, cores = 4, iter = 2000, warmup = 1000)

herb_brms <- brms::brm(n.herb ~ imp200m_s + WealthIndex_s + month + (1|site_code),
                         data = sites, 
                         family = negbinomial(link = "log"),
                       prior = priors_herb,
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)

enemy_brms <- brms::brm(n.enemy ~ imp200m_s + WealthIndex_s + month + (1|site_code),
                         data = sites, 
                         family = negbinomial(link = "log"), 
                        prior = priors_enemy,
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)
summary(pol_brms)
summary(herb_brms)
summary(enemy_brms)
#plot(pol_brms)
```

## Plots

Making site variables prediction grid
```{r}
wealth_ref <- mean(sites$WealthIndex, na.rm = TRUE)
imp_ref <- mean(sites$imp200m, na.rm = TRUE)

imp_center <- mean(sites$imp200m, na.rm = TRUE)
imp_scale  <- sd(sites$imp200m, na.rm = TRUE)

wealth_center <- mean(sites$WealthIndex, na.rm = TRUE)
wealth_scale  <- sd(sites$WealthIndex, na.rm = TRUE)

# Prediction grid for impervious surface
sitevar.pred.imp <- tidyr::expand_grid(
  imp200m = seq(
    min(sites$imp200m, na.rm = TRUE),
    max(sites$imp200m, na.rm = TRUE),
    length.out = 50
  ),
  site_code = unique(sites$site_code),
  month = unique(sites$month)
) %>%
  mutate(
    WealthIndex = wealth_ref,
    imp200m_s = (imp200m - imp_center) / imp_scale,
    WealthIndex_s = (WealthIndex - wealth_center) / wealth_scale
  )
```

#### Total Arthropod Abundance & Landscape Variables 
```{r, message=FALSE}
#Generate predictions on grid from arthropod brms model
arth.preds.imp <- sitevar.pred.imp %>%
  add_epred_draws(arthropods_brms, ndraws = 200)

arth.preds.wealth <- sitevar.pred.wealth %>%
  add_epred_draws(arthropods_brms, ndraws = 200)

#Total arthropod abundance and Impervious Surface with brms estimate with credible intervals
arth.imp.plot <- ggplot(arth.preds.imp, aes(x = imp200m, y = .epred)) +
  stat_lineribbon(.width = c(.95, .80, .50),
                  alpha = 0.5, colour = "black") +
  geom_point(data = sites,
             aes(x = imp200m, y = n.obs),
             colour = "darkseagreen4", size = 3) +
  scale_fill_brewer(palette = "Greys") +
  ylab("Total arthropod abundance") +
  xlab("Impervious surface 200 m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
arth.imp.plot 

#Total arthropod abundance and Wealth Inde
arth.wealth.plot <- ggplot(arth.preds.imp, aes(x = WealthIndex, y = .epred)) +
  geom_point(data = sites,
             aes(x = WealthIndex, y = n.obs),
             colour = "darkseagreen4", size = 3) +
  scale_fill_brewer(palette = "Greys") +
  ylab("Total arthropod abundance") +
  xlab("Wealth Index 500 m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
arth.wealth.plot 

#Effect size plot with credible intervals
effect_arthropods <- tibble(
  term = c("Impervious surface", "Wealth Index"),
  estimate = c(-0.49, 0.09),
  lower = c(-0.67,-0.09),
  upper = c(-0.31, 0.26)
)

effect.plot.arthropods <- ggplot(effect_arthropods, aes(x = term, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_linerange(aes(ymin = lower, ymax = upper), linewidth = 1, 
                 color = c("darkseagreen4", "gray")) +
  geom_point(size = 3,
             color = c("darkseagreen4", "gray")) +
  ylab("Beta estimate") +
  xlab(NULL) +
  theme_minimal() +
  Asia_Theme
effect.plot.arthropods

arthropods.panelplot <- ggarrange(arth.imp.plot, arth.wealth.plot, ncol = 2, labels = "AUTO")
```

### Pollinator Abundance and Landscape Variables
```{r, message=FALSE}
#Generate predictions on grid from pollinator brms model
pol.preds.imp <- sitevar.pred.imp %>%
  add_epred_draws(pol_brms, ndraws = 200)

#Pollinator abundance and Impervious Surface
pol.imp.plot <- ggplot(pol.preds.imp, aes(x = imp200m, y = .epred, color = month)) +
  geom_smooth()+
  geom_point(data = sites,
             aes(x = imp200m, y = n.pol, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
     scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Pollinator abundance") +
  xlab("Impervious surface 200 m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
pol.imp.plot

#Pollinator abundance and Wealth Index
pol.wealth.plot <- ggplot(pol.preds.imp, aes(x = WealthIndex, y = .epred, color = month)) +
  geom_point(data = sites,
             aes(x = WealthIndex, y = n.pol, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
     scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Pollinator abundance") +
  xlab("Wealth Index 500 m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
pol.wealth.plot

#Effect size plot with credible intervals
effect_pol <- tibble(
  term = factor(
    c("Impervious surface", "Wealth Index"),
    levels = c("Impervious surface", "Wealth Index")
  ),
  estimate = c(-0.53, 0.07),
  lower = c(-0.81, -0.17),
  upper = c(-0.24, 0.33)
)

effect.plot.pol <- ggplot(effect_pol, aes(x = term, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_linerange(aes(ymin = lower, ymax = upper), linewidth = 1, 
                 color = c("darkseagreen4", "gray")) +
  geom_point(size = 3,
             color = c("darkseagreen4", "gray")) +
  ylab("Beta estimate") +
  xlab(NULL) +
  theme_minimal() +
  Asia_Theme
effect.plot.pol
```

### Herbivore Abundance and Landscape Variables
```{r}
#Generate predictions on grid from herbivore brms model
herb.preds.imp <- sitevar.pred.imp %>%
  add_epred_draws(herb_brms, ndraws = 200)

#Herbivore abundance and Impervious Surface
herb.imp.plot <- ggplot(herb.preds.imp, aes(x = imp200m, y = .epred, color = month)) +
  geom_smooth() +
  geom_point(data = sites,
             aes(x = imp200m, y = n.herb, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
    scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Herbivore abundance") +
  xlab("Impervious surface 200 m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
herb.imp.plot

#Herbivore abundance and Wealth Index
herb.wealth.plot <- ggplot(herb.preds.imp, aes(x = WealthIndex, y = .epred,  color = month)) +
  geom_point(data = sites,
             aes(x = WealthIndex, y = n.herb, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
    scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Herbivore abundance") +
  xlab("Wealth Index 500 m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
herb.wealth.plot 

#effect size with credible intervals
effect_herb <- tibble(
  term = factor(
    c("Impervious surface", "Wealth Index"),
    levels = c("Impervious surface", "Wealth Index")
  ),
  estimate = c(-0.47, 0.07),
  lower = c(-0.79, -0.23),
  upper = c(-0.18, 0.35)
)

effect.plot.herb <- ggplot(effect_herb, aes(x = term, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_linerange(aes(ymin = lower, ymax = upper), linewidth = 1, 
                 color = c("darkseagreen4", "gray")) +
  geom_point(size = 3,
             color = c("darkseagreen4", "gray")) +
  ylab("Beta estimate") +
  xlab(NULL) +
  theme_minimal() +
  Asia_Theme
effect.plot.herb
```

### Natural Enemy Abundance and Landscape Variables
```{r}
#Generate predictions on grid from natural enemy brms model
enemy.preds.imp <- sitevar.pred.imp %>%
  add_epred_draws(enemy_brms, ndraws = 200)

#Natural Enemy abundance and Impervious Surface
enemy.imp.plot <- ggplot(enemy.preds.imp, aes(x = imp200m, y = .epred, color = month)) +
  geom_smooth() +
  geom_point(data = sites,
             aes(x = imp200m, y = n.enemy, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
    scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Natural Enemy abundance") +
  xlab("Impervious surface 200 m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
enemy.imp.plot

#Natural enemy abundance and Wealth Index
enemy.wealth.plot <- ggplot(enemy.preds.imp, aes(x = WealthIndex, y = .epred,  color = month)) +
  geom_point(data = sites,
             aes(x = WealthIndex, y = n.enemy, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
    scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Natural Enemy abundance") +
  xlab("Wealth Index 500 m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
enemy.wealth.plot 

#effect sizes with credible intervals
effect_enemy <- tibble(
  term = factor(
    c("Impervious surface", "Wealth Index"),
    levels = c("Impervious surface", "Wealth Index")
  ),
  estimate = c(-0.43, 0.08),
  lower = c(-0.64, -0.09),
  upper = c(-0.23, 0.25)
)

effect.plot.enemy <- ggplot(effect_enemy, aes(x = term, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_linerange(aes(ymin = lower, ymax = upper), linewidth = 1, 
                 color = c("darkseagreen4", "gray")) +
  geom_point(size = 3,
             color = c("darkseagreen4", "gray")) +
  ylab("Beta estimate") +
  xlab(NULL) +
  theme_minimal() +
  Asia_Theme
effect.plot.enemy
```

## Bee Species Richness
```{r}
bee.hist <- ggplot(sites, aes(x = bee.rich))+
    geom_histogram()+
    xlab("bee richness")+
    theme_minimal()+
    Asia_Theme
bee.hist #normally distributed within each month

#Test for non-linear response to wealth
gam_fit <- gam(bee.rich ~ s(WealthIndex) + imp200m + month,
               data = sites,
               family = gaussian(link = "identity"),
  method = "REML")
summary(gam_fit)
plot(gam_fit, pages = 1) #significant non-linear effect with wealth

set.seed(10)

#finding the peak (where relationship reverses) by comparing model fits

#   candidates <- seq(135, 175, by = 10)
#   fits <- list()
#   for (cp in candidates) {
#   dat <- sites
#   dat$WI_high_s <- pmax(dat$WealthIndex_s - cp, 0)
  
#  fits[[paste0("cp_", cp)]] <- brm(
#    bee.rich ~ imp200m_s + WealthIndex_s + WI_high + month + (1|site_code),
 #   data = sites,
  #  family = gaussian(),
   # chains = 2, cores = 2, iter = 2000, warmup = 1000,
    #refresh = 0)}
#loos <- lapply(fits, loo)
#loo_compare(loos)

bees_brms <- brms::brm(bee.rich ~ imp200m_s + WealthIndex_s + WI_high_s + month + (1|site_code),data = sites,  family = gaussian(), 
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)
summary(bees_brms)

```
Plots
```{r}
WI_high <- pmax(sites$WealthIndex - 155, 0)
WI_high_center <- mean(WI_high, na.rm = TRUE)
WI_high_scale  <- sd(WI_high, na.rm = TRUE)

# Prediction grid for impervious surface
sitevar.pred.imp <- tidyr::expand_grid(
  imp200m = seq(
    min(sites$imp200m, na.rm = TRUE),
    max(sites$imp200m, na.rm = TRUE),
    length.out = 50
  ),
  site_code = unique(sites$site_code),
  month = unique(sites$month)
) %>%
  mutate(
    WealthIndex = wealth_ref,
    WI_high = pmax(WealthIndex - 155, 0),
    imp200m_s = (imp200m - imp_center) / imp_scale,
    WealthIndex_s = (WealthIndex - wealth_center) / wealth_scale,
    WI_high_s = (WI_high - WI_high_center) / WI_high_scale
  )

# Prediction grid for wealth index
sitevar.pred.wealth <- tidyr::expand_grid(
  WealthIndex = seq(
    min(sites$WealthIndex, na.rm = TRUE),
    max(sites$WealthIndex, na.rm = TRUE),
    length.out = 50
  ),
  site_code = unique(sites$site_code),
  month = unique(sites$month)
) %>%
  mutate(
    imp200m = imp_ref,
    WI_high = pmax(WealthIndex - 155, 0),
    imp200m_s = (imp200m - imp_center) / imp_scale,
    WealthIndex_s = (WealthIndex - wealth_center) / wealth_scale,
    WI_high_s = (WI_high - WI_high_center) / WI_high_scale
  )

#Generate predictions on grid from bees brms model
bees.preds.imp  <- sitevar.pred.imp %>%
  add_epred_draws(bees_brms, ndraws = 200)

bees.preds.wealth <- sitevar.pred.wealth %>%
  add_epred_draws(bees_brms, ndraws = 200)


#Bee richness and Impervious Surface
bees.imp.plot <- ggplot(bees.preds.imp, aes(x = imp200m, y = .epred, color = month)) +
  geom_smooth() +
  geom_point(data = sites,
             aes(x = imp200m, y = bee.rich, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
        scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Rarefied bee richness") +
  xlab("Impervious surface 200 m") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.85))+
    Asia_Theme
bees.imp.plot

#Bee richness and Wealth Index
bees.wealth.plot <- ggplot(bees.preds.wealth, aes(x = WealthIndex, y = .epred, color = month)) +
  geom_smooth() +
  geom_point(data = sites,
             aes(x = WealthIndex, y = bee.rich, shape = month), size = 3) +
  scale_color_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month")+
        scale_shape_manual(values = c(
         "June" = 16,
         "July" = 15,
         "August" = 17), limits = c("June", "July", "August"), name = "Month") +
  ylab("Rarefied bee richness") +
  xlab("Wealth Index 500 m") +
  theme_minimal() +
  theme(legend.position = "none")+
    Asia_Theme
bees.wealth.plot 

#effect sizes with credible intervals
effect_bees <- tibble(
  term = factor(
    c("Impervious surface", "WI < 155", "WI slope change > 155"),
    levels = c("Impervious surface", "WI < 155", "WI slope change > 155")
  ),
  estimate = c(-3.32, 5.01, -6.46),
  lower = c(-5.31, 0.89, -10.47),
  upper = c(-1.32, 8.98, -2.38)
)

effect.plot.bees <- ggplot(effect_bees, aes(x = term, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_linerange(aes(ymin = lower, ymax = upper), linewidth = 1, 
                 color = c("darkseagreen4", "darkseagreen4","darkseagreen4")) +
  geom_point(size = 3,
             color = c("darkseagreen4", "darkseagreen4","darkseagreen4")) +
  ylab("Beta estimate") +
  xlab(NULL) +
  theme_minimal() +
  Asia_Theme
effect.plot.bees

bees.panelplot <- ggarrange(bees.imp.plot, bees.wealth.plot, effect.plot.bees, ncol = 3, labels = "AUTO",common.legend = TRUE)
```

Panel plot for all functional groups
```{r}
fungroup.panelplot <- ggarrange(pol.imp.plot, pol.wealth.plot, effect.plot.pol, herb.imp.plot, herb.wealth.plot, effect.plot.herb, enemy.imp.plot, enemy.wealth.plot,effect.plot.enemy,
        ncol = 3, nrow = 3, 
        labels = "AUTO",
        font.label = list(size = 25, face = "bold"),
        common.legend = TRUE)
```

# Cucumber Outcomes

Created dataset aggregated by summer
```{r}
#one full summer data set, summing arthropod values across months
sem_data <- sites%>%
    group_by(site_code)%>%
    summarise(n.herb = sum(n.herb),
              n.pol = sum(n.pol),
              n.enemy = sum(n.enemy),
              n.pred = sum(n.pred),
              WealthIndex = mean(WealthIndex),
              tcc200m = mean(tcc200m),
              tcc500m = mean(tcc500m),
              imp200m = mean(imp200m),
              wood_m2 = mean(wood_m2),
              bareground_m2 = mean(bareground_m2),
              floral_area_m2 = mean(floral_area_m2),
              shrub_grass1000m = mean(shrub_grass1000m),
              gbif.rich = mean(gbif.rich),
              gbif.shannon = mean(gbif.shannon),
              gbif.simpson = mean(gbif.simpson),
              flor.rich = mean(flor.rich),
              flor.shannon = mean(flor.shannon),
              flor.simpson = mean(flor.simpson),
              delta_mass = mean(delta_mass),
              delta_cylindrical = mean(delta_cylindrical),
              delta_length = mean(delta_length),
              delta_width = mean(delta_width),
              delta_volume = mean(delta_volume),
              delta_seed_mass_ratio = mean(delta_seed_mass_ratio),
              delta_no = mean(delta_no),
              n.obs = sum(n.obs),
              bee.rich = sum(bee.rich),
              bee.shannon = sum(bee.shannon),
              bee.simpson = sum(bee.simpson),
              water_wetland_1000m = mean(water_wetland_1000m),
              species_per_m2 = mean(species_per_m2),
              imp200m_s = mean(imp200m_s),
              WealthIndex_s = mean(WealthIndex_s),
              WI_high = mean(WI_high),
              WI_high_s = mean(WI_high_s)
    )
sem_data             
```

Explore cucumber outcome data for normality
```{r}
c_outcomes <- c("delta_seed_mass_ratio", "delta_mass", "delta_cylindrical", "delta_no", "delta_length", "delta_width", "delta_volume") 

for (i in c_outcomes) {
  print(i)
  print(shapiro.test(sem_data[[i]]))
}
```

## Structural Equation Modelling 

Put arthropod mediator models in correct format
```{r}
bf_pol   <- bf(n.pol   ~ imp200m_s + WealthIndex_s,
               family = negbinomial())
bf_herb  <- bf(n.herb  ~ imp200m_s + WealthIndex_s,
               family = negbinomial())
bf_enemy <- bf(n.enemy ~ imp200m_s + WealthIndex_s,
               family = negbinomial())
bf_bee   <- bf(bee.shannon ~ imp200m_s + WealthIndex_s,
               family = gaussian())

#priors for cucumber outcomes
prior(normal(0,1), class = "b", coef = "bee.rich")


#Cucumber outcome model
bf_cuc <- bf(delta_no ~ 
                bee.shannon + WealthIndex_s + imp200m_s,
              family = student())
```


Structural Equation Model
```{r}
set.seed(100)

fit_sem <- brm(
  bf_bee + bf_cuc +
    set_rescor(FALSE),
  data = sem_data,
  chains = 4, cores = 4
)

summary(fit_sem)

post <- posterior_samples(fit_sem)
```


## Plots

### Cucumbers and Bee Richness
```{r}
cuc.beerich.plot1 <- ggplot(sem_data, aes(x = bee.rich, y = delta_seed_mass_ratio))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beerich.plot1 

cuc.beerich.plot2 <- ggplot(sem_data, aes(x = bee.rich, y = delta_no))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beerich.plot2 

cuc.beerich.plot3 <- ggplot(sem_data, aes(x = bee.rich, y = delta_cylindrical))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beerich.plot3 

cuc.beerich.plot4 <- ggplot(sem_data, aes(x = bee.rich, y = delta_mass))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beerich.plot4
```

### Cucumbers and Bee Shannon Diversity
```{r}
cuc.beeshan.plot1 <- ggplot(sem_data, aes(x = bee.shannon, y = delta_seed_mass_ratio))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beeshan.plot1 

cuc.beeshan.plot2 <- ggplot(sem_data, aes(x = bee.shannon , y = delta_no))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beeshan.plot2 

cuc.beeshan.plot3 <- ggplot(sem_data, aes(x = bee.shannon, y = delta_cylindrical))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beeshan.plot3 

cuc.beeshan.plot4 <- ggplot(sem_data, aes(x = bee.shannon, y = delta_mass))+
    geom_point()+
    geom_smooth(method = "lm")
cuc.beeshan.plot4
```

Number of cucumbers and bee shannon diversity
```{r}
set.seed(1)
cuc_brms <- brms::brm(delta_no ~ bee.shannon,  family = student(), 
                      data = sem_data,
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)
summary(cuc_brms)
```
Bee shannon diversity and no of cucumbers plot
```{r}
#Generate predictions on grid from brms model
pred_grid <- tibble(
  bee.shannon = seq(
    min(sem_data$bee.shannon, na.rm = TRUE),
    max(sem_data$bee.shannon, na.rm = TRUE),
    length.out = 100
  )
)

cuc.preds <- pred_grid %>%
  add_epred_draws(cuc_brms, ndraws = 200)


#Cucumbers and bee shannon diversity with brms estimate with credible intervals
cuc.plot <- ggplot(cuc.preds, aes(x = bee.shannon, y = .epred)) +
  stat_lineribbon(.width = c(.95, .80, .50),
                  alpha = 0.5, colour = "black") +
  geom_point(data = sem_data,
             aes(x = bee.shannon, y = delta_no),
             colour = "darkseagreen4", size = 3) +
  scale_fill_brewer(palette = "Greys") +
  ylab("delta cucumber abundance n/
       (control - hand pollinated)") +
  xlab("rarefied bee shannon diversity") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.85, 0.15))+
    Asia_Theme
cuc.plot 
```

# Habitat Quality

Look at the relationship between local and landscape variable and wealth index

Local variables
```{r}
set.seed(1)
wood_brms <- brms::brm(wood_m2 ~ WealthIndex,  family = student(), 
                      data = sem_data,
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)

bareground_brms <- brms::brm(bareground_m2 ~ WealthIndex,  family = student(), 
                      data = sem_data,
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)

flor_brms <- brms::brm(flor.rich ~ WealthIndex,  family = gaussian(), 
                      data = sem_data,
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)

flor_density_brms <- brms::brm(species_per_m2 ~ WealthIndex,  family = student(), 
                      data = sem_data,
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)


summary(wood_brms)
summary(flor_brms)
summary(bareground_brms)
summary(flor_density_brms)
```

Landscape variables
```{r}
set.seed(1)
tcc_brms <- brms::brm(tcc500m ~ WealthIndex,  family = student(), 
                      data = sem_data,
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)

gbif_brms <- brms::brm(gbif.rich ~ WealthIndex,  family = student(), 
                      data = sem_data,
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)

water_wetland_brms <- brms::brm(water_wetland_1000m ~ WealthIndex,  family = gaussian(), 
                      data = sem_data,
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)

shrub_grassland_brms <- brms::brm(shrub_grass1000m ~ WealthIndex,  family = student(), 
                      data = sem_data,
                         chains = 3, cores = 4, iter = 2000, warmup = 1000)


summary(tcc_brms)
summary(gbif_brms)
summary(water_wetland_brms)
summary(shrub_grassland_brms)
```


# Save Images
```{r}
ggsave("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/figures/Arthropods_PanelFig.pdf", plot = arthropods.panelplot, height = 6, width = 10)

ggsave("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/figures/Bees_PanelFig.pdf", plot = bees.panelplot, height = 6, width = 12)

ggsave("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/figures/FunctionalGroups_PanelFig.pdf", plot = fungroup.panelplot, height = 12, width = 12)

ggsave("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/figures/Cucumber_plot.pdf", plot = cuc.plot, height = 6, width = 6)
```

