---
title: "Analyses - Community Composition and Structural Equation Modelling"
output: html_document
date: "2026-01-20"
---

# Load Packages
```{r, message=FALSE}
library("tidyverse")
library("lme4")
library("lmerTest")
library("vegan")
library("corrplot")
library("Hmisc")
```

# Read in the Data
```{r, warning=FALSE}
#Clear environment
rm(list = ls())

setwd("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research")

#all site data
sites <- read.csv("data/sites_all.csv")
```

Making needed variables
```{r}
sites <- sites %>%
    mutate(water_wetland_1000m = water1000m + wetland1000m,
           n.enemy = n.pred + n.omn,
           species_per_m2 = flor.rich/floral_area_m2)
```


GGplot Theme
```{r}
Asia_Theme <- theme(
  plot.title = element_text(size = 16),
  plot.caption = element_text(size = 16),
  axis.title = element_text(size = 18),
  axis.text = element_text(size = 16),
  axis.text.x = element_text(size = 20),
  legend.text = element_text(size= 20))
```

# Habitat Quality and Environmental Variables

## Landscape Level Variables

Landscape Level Correlations
```{r}
#Landscape variables
site.landscape.input <- sites %>% select(-c(Site,site_code)) %>%
    select(WealthIndex, tcc200m, imp200m, tcc500m,imp500m,water1000m, wetland1000m, shrub_grass1000m)

#Landscape correlation test
landscape.rcorr = rcorr(as.matrix(site.landscape.input))
landscape.pvals <- landscape.rcorr$P

#Correlation plot
landscape.cor.plot <- corrplot(landscape.rcorr$r)
```

## Wealth and Landscape Variables Relationships
```{r}
#GBIF Landscape floral richness
wealth.land.plot1 <- ggplot(sites, aes(x = WealthIndex, y = gbif.rich))+
    geom_point()+
    ylab("Landscape floral richness (1 km)")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.land.plot1

#Tree canopy cover
wealth.land.plot2 <- ggplot(sites, aes(x = WealthIndex, y = tcc500m))+
    geom_point()+
    ylab("Tree Canopy Cover (500 m)")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.land.plot2

#Shrubland Cover
wealth.land.plot3 <- ggplot(sites, aes(x = WealthIndex, y = shrub_grass1000m))+
    geom_point()+
    ylab("Shrub & Grassland (1 km)")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.land.plot3

#Wetland Cover
wealth.land.plot4 <- ggplot(sites, aes(x = WealthIndex, y = water_wetland_1000m))+
    geom_point()+
    ylab("Water and Wetland (1 km)")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.land.plot4
```

## Wealth and Local Variables Relationships
```{r}
#Garden floral richness
wealth.loc.plot1 <- ggplot(sites, aes(x = WealthIndex, y = flor.simpson))+
    geom_point()+
    ylab("Garden floral richness")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.loc.plot1

#Garden Tree and Shrub Cover
wealth.loc.plot2 <- ggplot(sites, aes(x = WealthIndex, y = wood_m2))+
    geom_point()+
    ylab("Garden Tree and Shrub Cover")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.loc.plot2

#Garden Bareground Cover
wealth.loc.plot3 <- ggplot(sites, aes(x = WealthIndex, y = bareground_m2))+
    geom_point()+
    ylab("Garden Bareground Cover")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.loc.plot3

#Garden Bareground Cover
wealth.loc.plot4 <- ggplot(sites, aes(x = WealthIndex, y = species_per_m2))+
    geom_point()+
    ylab("Garden Floral Species/m2")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
wealth.loc.plot4
```
# Arthropod Abundance

## Total Arthropod Abundance & Landscape Variables
```{r}
#Total arthropod abundance and Impervious Surface
total.arth.imp.plot <- ggplot(sites, aes(x = imp200m, y = n.obs))+
    geom_point()+
    facet_wrap(vars(month), ncol = 3)+
    ylab("Total arthropod abundance")+
    xlab("Impervious surface (200 m)")+
    theme_minimal()+
    Asia_Theme
total.arth.imp.plot

#Total arthropod abundance and Wealth Index
total.arth.wealth.plot <- ggplot(sites, aes(x = WealthIndex, y = n.obs))+
    geom_point()+
    facet_wrap(vars(month), ncol = 3)+
    ylab("Total arthropod abundance")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
total.arth.wealth.plot
```
### Pollinator Abundance and Landscape Variables
```{r}
#Pollinator abundance and Impervious Surface
pol.imp.plot <- ggplot(sites, aes(x = imp200m, y = n.pol))+
    geom_point()+
    facet_wrap(vars(month), ncol = 3)+
    ylab("Pollinator abundance")+
    xlab("Impervious surface (200 m)")+
    theme_minimal()+
    Asia_Theme
pol.imp.plot

#Pollinator abundance and Wealth Index
pol.wealth.plot <- ggplot(sites, aes(x = WealthIndex, y = n.pol))+
    geom_point()+
    facet_wrap(vars(month), ncol = 3)+
    ylab("Pollinator abundance")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
pol.wealth.plot
```
### Herbivore Abundance and Landscape Variables
```{r}
#Pollinator abundance and Impervious Surface
herb.imp.plot <- ggplot(sites, aes(x = imp200m, y = n.herb))+
    geom_point()+
    facet_wrap(vars(month), ncol = 3)+
    ylab("Herbivore abundance")+
    xlab("Impervious surface (200 m)")+
    theme_minimal()+
    Asia_Theme
herb.imp.plot

#Pollinator abundance and Wealth Index
herb.wealth.plot <- ggplot(sites, aes(x = WealthIndex, y = n.herb))+
    geom_point()+
    facet_wrap(vars(month), ncol = 3)+
    ylab("Herbivore abundance")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
herb.wealth.plot
```

### Natural Enemy Abundance and Landscape Variables
```{r}
#Pollinator abundance and Impervious Surface
enemy.imp.plot <- ggplot(sites, aes(x = imp200m, y = n.enemy))+
    geom_point()+
    facet_wrap(vars(month), ncol = 3)+
    ylab("Natural enemy abundance")+
    xlab("Impervious surface (200 m)")+
    theme_minimal()+
    Asia_Theme
enemy.imp.plot

#Pollinator abundance and Wealth Index
enemy.wealth.plot <- ggplot(sites, aes(x = WealthIndex, y = n.enemy))+
    geom_point()+
    facet_wrap(vars(month), ncol = 3)+
    ylab("Natural enemy abundance")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
enemy.wealth.plot
```
### Detritivore Abundance and Landscape Variables
```{r}
#Pollinator abundance and Impervious Surface
det.imp.plot <- ggplot(sites, aes(x = imp200m, y = n.det))+
    geom_point()+
    facet_wrap(vars(month), ncol = 3)+
    ylab("Detritivore abundance")+
    xlab("Impervious surface (200 m)")+
    theme_minimal()+
    Asia_Theme
det.imp.plot

#Pollinator abundance and Wealth Index
det.wealth.plot <- ggplot(sites, aes(x = WealthIndex, y = n.det))+
    geom_point()+
    facet_wrap(vars(month), ncol = 3)+
    ylab("Natural enemy abundance")+
    xlab("Wealth Index (500 m)")+
    theme_minimal()+
    Asia_Theme
det.wealth.plot
```
# Habitat Quality Index
```{r}

```

# Structural Equation Modelling
```{r}

```

