---
title: "Analyses - Community Composition"
output: html_document
date: "2026-01-20"
---

# Load Packages
```{r, message=FALSE}
library("tidyverse")
library("lme4")
library("lmerTest")
library("vegan")
library("corrplot")
library("Hmisc")
library("viridis")
library("ggpubr")
```

# Read in the Data
```{r, warning=FALSE}
#Clear environment
rm(list = ls())

setwd("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research")

#all site data
sites <- read.csv("data/sites_all.csv")

#matrix data for community analyses
inat_wide <- read.csv("data/inat_wide.csv")
arthropods_wide <- read.csv("data/arthropods_wide.csv")
arthropods_wide_sum <- read.csv("data/arthropods_wide_sum.csv")
gbif_wide <- read.csv("data/gbif_fam_wide.csv")
bees <- read.csv("data/bees.csv")
bees_agg <- read.csv("data/bees_agg.csv")
```

# Explore the Data
```{r}

```

GGplot Theme
```{r}
Asia_Theme <- theme(
  plot.title = element_text(size = 16),
  plot.caption = element_text(size = 16),
  axis.title = element_text(size = 20),
  axis.text = element_text(size = 16),
  axis.text.x = element_text(size = 20),
  legend.text = element_text(size= 11))
```



# Community Composition

Site covariates of interest for NMDS plots & mantel test
```{r}
site_cov <- sites %>%
    filter(month == "June")%>%
    select(c("site_code","tcc200m","imp200m","tcc500m","imp500m","WealthIndex","floral_area_m2","flor.rich"))
```

## Garden Floral NMDS
```{r, echo=FALSE}
set.seed(10)
florNMDS_input <- inat_wide[,-1]
florNMDS_input <- florNMDS_input[, colSums(florNMDS_input > 0) >= 10]

flor.mds <- metaMDS(florNMDS_input, k = 2, trymax = 20)
flor.mds

#Make nmds into dataframe for plotting
flor.mds.scores <- as.data.frame(scores(flor.mds, display = "sites"))
flor.mds.scores <- cbind(flor.mds.scores, site_cov)
```

Garden Floral Community NMDS Plot
```{r}
flor.mds.scores$WealthStrata <- cut(
  flor.mds.scores$WealthIndex,
  breaks = c(-Inf, 100, 150, Inf),
  labels = c("Low wealth (< 100)", "Moderate wealth (100 - 150)", "High wealth (>150)"),
  include.lowest = TRUE)


flor.mds.plot <- 
  ggplot(flor.mds.scores, aes(NMDS1, NMDS2)) +
  geom_polygon(data = flor.mds.scores %>%
    group_by(WealthStrata) %>%
    slice(chull(NMDS1, NMDS2)),aes(fill = WealthStrata, group = WealthStrata), alpha = 0.22, color = NA, show.legend = FALSE) +
  geom_point(aes(fill = WealthStrata, shape = WealthStrata),
    color = "black",
    size = 3,
    stroke = 0.6) +
  scale_fill_viridis_d(
    option = "viridis",
    limits = c("Low wealth (< 100)","Moderate wealth (100 - 150)","High wealth (>150)"),
    begin = 0,
    end = 1,
    name = "Wealth Index") +
    scale_shape_manual(
    values = c(21, 22, 24),   # all filled shapes
    limits = c(
      "Low wealth (< 100)","Moderate wealth (100 - 150)","High wealth (>150)"),
    name = "Wealth Index") +
  theme_minimal() +
  labs(title = "Local Flora",
    x = "NMDS1",
    y = "NMDS2") +
    Asia_Theme+
    theme(legend.position = "none", aspect.ratio = 1)+
    coord_fixed(ratio = 1)
flor.mds.plot
```

## Landscape NMDS Floral Families
```{r, echo=FALSE}
set.seed(10)
landNMDS_input <- gbif_wide[,-1]
landNMDS_input <- landNMDS_input[, colSums(landNMDS_input > 0) >= 7]

land.mds <- metaMDS(landNMDS_input, k = 2, trymax = 20)
land.mds

#Make nmds into dataframe for plotting
land.mds.scores <- as.data.frame(scores(land.mds, display = "sites"))
land.mds.scores <- cbind(land.mds.scores, site_cov)
```

Landscape Level Floral Community NMDS Plot
```{r}
land.mds.scores$WealthStrata <- cut(
  land.mds.scores$WealthIndex,
  breaks = c(-Inf, 100, 150, Inf),
  labels = c("Low wealth (< 100)", "Moderate wealth (100 - 150)", "High wealth (>150)"),
  include.lowest = TRUE)


land.mds.plot <- 
  ggplot(land.mds.scores, aes(NMDS1, NMDS2)) +
  geom_polygon(data = land.mds.scores %>%
    group_by(WealthStrata) %>%
    slice(chull(NMDS1, NMDS2)),aes(fill = WealthStrata, group = WealthStrata), alpha = 0.22, color = NA,show.legend = FALSE) +
  geom_point(aes(fill = WealthStrata, shape = WealthStrata),
    color = "black",
    size = 3,
    stroke = 0.6) +
  scale_fill_viridis_d(
    option = "viridis",
    limits = c("Low wealth (< 100)","Moderate wealth (100 - 150)","High wealth (>150)"),
    begin = 0,
    end = 1,
    name = "Wealth Index") +
    scale_shape_manual(
    values = c(21, 22, 24),   # all filled shapes
    limits = c(
      "Low wealth (< 100)","Moderate wealth (100 - 150)","High wealth (>150)"),
    name = "Wealth Index") +
  theme_minimal() +
  labs(title = "Landscape Flora",
    x = "NMDS1",
    y = "NMDS2") +
    Asia_Theme+
    theme(legend.position = "none", aspect.ratio = 1)+
    coord_fixed(ratio = 1)
land.mds.plot
```

## Arthropod Functional Groups NMDS
```{r, echo=FALSE}
set.seed(100)
arthropodsNMDS_input <- arthropods_wide[,-1]
arthropodsNMDS_input <- arthropodsNMDS_input[, colSums(arthropodsNMDS_input > 0) >= 30] # remove uncommon taxa to reduce stress
arthropodsNMDS_input <- arthropodsNMDS_input %>% select(-Unknown)

arthropods.mds <- metaMDS(arthropodsNMDS_input, trymax = 50)
arthropods.mds

#make nmds into dataframe for plotting
arthropods.mds.scores <- as.data.frame(scores(arthropods.mds, display = "sites"))
arthropods_columns <- arthropods_wide %>%
    separate(site_month, into = c("site", "month"), sep = "_")%>%
    select(site,month)%>%
    mutate(site_code = site)

arthropods.mds.scores$site_code <- arthropods_columns$site_code
arthropods.mds.scores$month <- arthropods_columns$month
arthropods.mds.scores <-left_join(arthropods.mds.scores, site_cov, by = "site_code")
```

Arthropod Functional Groups NMDS Plot by Month
```{r}
arthropods.mds.plot <- 
  ggplot(arthropods.mds.scores, aes(NMDS1, NMDS2)) +
  geom_polygon(data = arthropods.mds.scores %>%
    group_by(month) %>%
    slice(chull(NMDS1, NMDS2)),aes(fill = month, group = month), alpha = 0.22, color = NA,show.legend = FALSE) +
  geom_point(aes(fill = month, shape = month),
    color = "black",
    size = 3,
    stroke = 0.6) +
  scale_fill_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month") +
    scale_shape_manual(
    values = c(21, 22, 24),   # all filled shapes
    limits = c("June","July","August"),
    name = "Month") +
  theme_minimal() +
    Asia_Theme+
  labs(title = "Arthropod Functional Groups",
    x = "NMDS1",
    y = "NMDS2") +
    theme(legend.position = "none", aspect.ratio = 1)
    coord_fixed(ratio = 1)
arthropods.mds.plot
```

Arthropod NMDS for Aggregated Summer Data
```{r}
set.seed(10)

arthropods.sum.NMDS_input <- arthropods_wide_sum[,-1]
arthropods.sum.NMDS_input <- arthropods.sum.NMDS_input[, colSums(arthropods.sum.NMDS_input > 0) >= 5]

arthropods.sum.mds <- metaMDS(arthropods.sum.NMDS_input, k = 2, trymax = 30)
arthropods.sum.mds

arthropods.sum.mds.scores <- as.data.frame(scores(arthropods.sum.mds, display = "sites"))

#Make nmds into dataframe for plotting
arthropods.sum.mds.scores$site_code <- arthropods_wide_sum$site_code
arthropods.sum.mds.scores <-left_join(arthropods.sum.mds.scores, site_cov, by = "site_code")
```

Arthropods NMDS Plot for Full Summer Data
```{r}
arthropods.sum.mds.scores$WealthStrata <- cut(
  arthropods.sum.mds.scores$WealthIndex,
  breaks = c(-Inf, 100, 150, Inf),
  labels = c("Low wealth (< 100)", "Moderate wealth (100 - 150)", "High wealth (>150)"),
  include.lowest = TRUE)


arthropods.sum.mds.plot <- 
  ggplot(arthropods.sum.mds.scores, aes(NMDS1, NMDS2)) +
  geom_polygon(data = arthropods.sum.mds.scores %>%
    group_by(WealthStrata) %>%
    slice(chull(NMDS1, NMDS2)),aes(fill = WealthStrata, group = WealthStrata), alpha = 0.22, color = NA, show.legend = FALSE) +
  geom_point(aes(fill = WealthStrata, shape = WealthStrata),
    color = "black",
    size = 3,
    stroke = 0.6) +
  scale_fill_viridis_d(
    option = "viridis",
    limits = c("Low wealth (< 100)","Moderate wealth (100 - 150)","High wealth (>150)"),
    begin = 0,
    end = 1,
    name = "Wealth Index") +
    scale_shape_manual(
    values = c(21, 22, 24),   # all filled shapes
    limits = c(
      "Low wealth (< 100)","Moderate wealth (100 - 150)","High wealth (>150)"),
    name = "Wealth Index") +
  theme_minimal() +
  labs(title = "Arthropod Functional Groups",
    x = "NMDS1",
    y = "NMDS2") +
    Asia_Theme+
    theme(legend.position = "none", aspect.ratio = 1)+
    coord_fixed(ratio = 1)
arthropods.sum.mds.plot
```

## Bee Species NMDS
```{r}
set.seed(10)
bees_wide <- bees %>%
  mutate(site_month = paste(site_code, month, sep = "_"))%>%
    pivot_wider(
    id_cols = site_month,
    names_from = spec_ID,
    values_from = spec.obs,
    values_fill = 0)

beesNMDS_input <- bees_wide[,-1]

bees.mds <- metaMDS(beesNMDS_input, k = 2, trymax = 20)

bees.mds

bees.mds.scores <- as.data.frame(scores(bees.mds, display = "sites"))
bees_columns <- bees_wide %>%
    separate(site_month, into = c("site", "month"), sep = "_")%>%
    select(site,month)%>%
    mutate(site_code = site)

#Make nmds into dataframe for plotting
bees.mds.scores$site_code <- bees_columns$site_code
bees.mds.scores$month <- bees_columns$month
bees.mds.scores <-left_join(bees.mds.scores, site_cov, by = "site_code")
```
Bees NMDS Plot by Month
```{r}
bees.mds.plot <- 
  ggplot(bees.mds.scores, aes(NMDS1, NMDS2)) +
  geom_polygon(data = bees.mds.scores %>%
    group_by(month) %>%
    slice(chull(NMDS1, NMDS2)),aes(fill = month, group = month), alpha = 0.22, color = NA,show.legend = FALSE) +
  geom_point(aes(fill = month, shape = month),
    color = "black",
    size = 3,
    stroke = 0.6) +
  scale_fill_viridis_d(
    option = "magma",
    limits = c("June","July","August"),
    begin = 0.1,
    end = .9,
    name = "Month") +
    scale_shape_manual(
    values = c(21, 22, 24),   # all filled shapes
    limits = c("June","July","August"),
    name = "Month") +
  theme_minimal() +
  labs(title = "Bee Species",
    x = "NMDS1",
    y = "NMDS2") +
    Asia_Theme+
    theme(legend.position = "none", aspect.ratio = 1)+
    coord_fixed(ratio = 1)
bees.mds.plot
```

Bee NMDS for Aggregated Summer Data
```{r}
set.seed(10)
bees_agg_wide <- bees_agg %>%
    pivot_wider(
    id_cols = site_code,
    names_from = spec_ID,
    values_from = spec.obs,
    values_fill = 0)

bees.agg.NMDS_input <- bees_agg_wide[,-1]
bees.agg.NMDS_input <- bees.agg.NMDS_input[, colSums(bees.agg.NMDS_input > 0) >= 2]

bees.agg.mds <- metaMDS(bees.agg.NMDS_input, k = 2, trymax = 30)
bees.agg.mds

bees.agg.mds.scores <- as.data.frame(scores(bees.agg.mds, display = "sites"))

#Make nmds into dataframe for plotting
bees.agg.mds.scores$site_code <- bees_agg_wide$site_code
bees.agg.mds.scores <-left_join(bees.agg.mds.scores, site_cov, by = "site_code")
```

Bee NMDS Plot for Full Summer Data
```{r}
bees.agg.mds.scores$WealthStrata <- cut(
  bees.agg.mds.scores$WealthIndex,
  breaks = c(-Inf, 100, 150, Inf),
  labels = c("Low wealth (< 100)", "Moderate wealth (100 - 150)", "High wealth (>150)"),
  include.lowest = TRUE)


bees.agg.mds.plot <- 
  ggplot(bees.agg.mds.scores, aes(NMDS1, NMDS2)) +
  geom_polygon(data = bees.agg.mds.scores %>%
    group_by(WealthStrata) %>%
    slice(chull(NMDS1, NMDS2)),aes(fill = WealthStrata, group = WealthStrata), alpha = 0.22, color = NA, show.legend = FALSE) +
  geom_point(aes(fill = WealthStrata, shape = WealthStrata),
    color = "black",
    size = 3,
    stroke = 0.6) +
  scale_fill_viridis_d(
    option = "viridis",
    limits = c("Low wealth (< 100)","Moderate wealth (100 - 150)","High wealth (>150)"),
    begin = 0,
    end = 1,
    name = "Wealth Index") +
    scale_shape_manual(
    values = c(21, 22, 24),   # all filled shapes
    limits = c(
      "Low wealth (< 100)","Moderate wealth (100 - 150)","High wealth (>150)"),
    name = "Wealth Index") +
  theme_minimal() +
  labs(title = "Bee Species",
    x = "NMDS1",
    y = "NMDS2") +
    Asia_Theme+
    theme(legend.position = "none", aspect.ratio = 1)+
    coord_fixed(ratio = 1)
bees.agg.mds.plot
```

# Mantel Tests
To test for significant correlations between continuous variables and site matrices (community data)

Garden-Level Floral Community
```{r}

```

Landscape Level Floral Community
```{r}

```

Arthropod Functional Group Community
```{r}

```

Bee Species Community
```{r}

```

# Save Figures
```{r}
Floral.nmds.plots <- ggarrange(flor.mds.plot,land.mds.plot,
                    labels = c("A","B"), nrow = 1, ncol = 2)
ggsave("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/figures/FloralNMDSFig.png", plot = Floral.nmds.plots, height = 7, width = 13)
```

