---
title: "Data Cleaning"
output: html_document
date: "2025-08-29"
---

# Load Packages
```{r}
library("tidyverse")
library("lme4")
library("lmerTest")
library("iNEXT")
library("sf")
library("units")
library("vegan")
```

# Read in the Data
```{r}
#Clear environment
rm(list = ls())

#Load in all datasets
setwd("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research")
arthropods_jun_raw <- read.csv("data/Arthropod Data - June - Traps.csv", na.strings = c("", " "))
arthropods_jul_raw <- read.csv("data/Arthropod Data - July - Traps.csv", na.strings = c("", " "))
arthropods_aug_raw <- read.csv("data/Arthropod Data - August - Traps.csv", na.strings = c("", " "))
cucumbers_raw <- read.csv("data/cucumber_data.csv", na.strings = c("", " "))
sites_raw <- read.csv("data/DUG_data - fall_data.csv", na.strings = c("", " "))
inat_raw <- read.csv("data/observations-672273.csv", na.strings = c("", " "))

#Joining arthropod month datasets
arthropods <- rbind(arthropods_jun_raw, arthropods_jul_raw)
arthropods <-rbind(arthropods,arthropods_aug_raw)
```

# Explore the data
```{r}
#str(arthropods)
#str(cucumbers_raw)
#str(sites_raw)
```
# Data Cleaning 

Select subset of site variables
```{r}
#Select which site level variables you want to keep in dataframe
sites <- sites_raw %>%
    select(Site, site_code, Area_m2, Plots, WealthIndex, tcc200m, imp200m, tcc500m, imp500m,CWD_m2,wood_m2,FWD_m2,logs,bareground_m2,floral_area_m2)
str(sites)
```

Descriptive statistics of site level variables
```{r}
site_statistics <- sites %>%
  summarise(across(c(Area_m2, Plots, WealthIndex, tcc200m, imp200m),
                   list(mean = ~mean(.x, na.rm = TRUE),
                        sd   = ~sd(.x, na.rm = TRUE)),
                   .names = "{.fn}_{.col}"))%>%
    pivot_longer(everything(),
               names_to = c("stat", "variable"),
               names_sep = "_") %>%
    pivot_wider(names_from = variable, values_from = value)
site_statistics 
```
Assign iNaturalist floral observations to sites
```{r}
#Convert iNaturalist data to an sf object
#Create buffer distances

#Convert gbif to sf points
sf_data <- st_as_sf(inat_raw, coords = c("longitude", "latitude"), crs = 4326)

#Convert cities.test to sf points
gardens.sf <- st_as_sf(sites_raw, coords = c("Long", "Lat"), crs = 4326)

#Create 45 km buffers around all cities
buffer_distance <- set_units(500, "m")  # 45 km in meters
gardens.buffer <- st_buffer(gardens.sf, dist = buffer_distance)
```

Assign all observations to a city
```{r}
# Perform spatial join: assign City to points within buffer
sf_data <- st_join(sf_data, gardens.buffer["site_code"], join = st_within)

# Fill points outside any city buffer
sf_data$site_code <- sf_data$site_code # Copy joined column

#Adding site codes for all chive (allium) observations manually since it was geo-obscured by iNat
manual_sites <- c(`81`="PAL", `183`="PAL", `202`="PAL", `637`="SLA", `649`="EDI",
                  `664`="EDI", `905`="EDI", `985`="SHO", `1005`="GW", `1012`="GW",
                  `1354`="RUB", `1356`="RUB", `1578`="SAM", `1640`="GABL",
                  `2101`="APP", `2202`="SLA", `2211`="SLA", `2214`="SLA",
                  `2446`="SHO", `2486`="CHA", `2511`="CHA")

sf_data$site_code[as.integer(names(manual_sites))] <- manual_sites


# Convert back to data frame if needed
inat_data <- as.data.frame(sf_data)

# Check unique city assignments
unique(inat_data$site_code)
```

Add floral observation abundance to site data
```{r}
## Group Summaries

# No. of observations
inat.obs.all <- inat_data %>%
  group_by(site_code) %>%
  summarise(floral.obs = n())

# Merge into site datasheet
sites <- sites %>%
  left_join(inat.obs.all, by = "site_code")

# Quick check
summary(sites)
```

# Floral Biodiversity Metrics
### Extracting Biodiversity Values

* Summarize species counts per site
* Pivot dataframe wide to get into correct format for iNEXT
* Run iNEXT for estimated richness and diversity values
* Add values back to city dataframe

```{r}
# Prepare iNaturalist data and convert to wide format
inat_wide <- inat_data %>%
  count(site_code,scientific_name) %>%
  pivot_wider(names_from = site_code, values_from = n, values_fill = 0)

# Prepare iNEXT input data
inat.iNEXTinput <- as.data.frame(inat_wide[,-1])

# Run iNEXT to find richness data
inat.iNEXT <- iNEXT(inat.iNEXTinput, q = 0, datatype = "abundance")

# Extract richness and diversity data
inat_richness <-  inat.iNEXT$AsyEst[inat.iNEXT$AsyEst$Diversity == "Species richness",]
inat_shannon <-  inat.iNEXT$AsyEst[inat.iNEXT$AsyEst$Diversity == "Shannon diversity",]
inat_simpson <-  inat.iNEXT$AsyEst[inat.iNEXT$AsyEst$Diversity == "Simpson diversity",]

# Match site_code to Assemblage
sites$flor.rich    <- inat_richness$Observed[match(sites$site_code, inat_richness$Assemblage)]
sites$flor.shannon <- inat_shannon$Observed[match(sites$site_code, inat_shannon$Assemblage)]
sites$flor.simpson <- inat_simpson$Observed[match(sites$site_code, inat_simpson$Assemblage)]
```

# Cucumber Data
```{r}
#Average cucumber values by treatment by site
cucumbers_avg <- cucumbers_raw %>%
    mutate(seed_mass_ratio = no_seeds/mass_g)%>%
    group_by(site_code, treatment) %>%
    summarise(
        avg_mass = mean(mass_g, na.rm = TRUE),
        avg_seeds = mean(no_seeds, na.rm = TRUE),
        avg_length = mean(length_mm, na.rm = TRUE),
        avg_width = mean(width, na.rm = TRUE),
        avg_volume = mean(volume_mL, na.rm = TRUE),
        prop_cylindrical = mean(cylindrical == "Yes", na.rm = TRUE),
        avg_seed_mass_ratio = mean(seed_mass_ratio, na.rm = TRUE))
cucumbers_avg
 
#Difference (Pollinated - Control) for cucumber values by site
cucumbers_delta <-  cucumbers_avg %>%
   arrange(site_code, treatment) %>% 
    group_by(site_code) %>%
  summarise(
    delta_mass  = diff(avg_mass),
    delta_seeds = diff(avg_seeds),
    delta_length = diff(avg_length),
    delta_width = diff(avg_width),
    delta_volume = diff(avg_volume),
    delta_cylindrical = diff(prop_cylindrical),
    delta_seed_mass_ratio = diff(avg_seed_mass_ratio))
cucumbers_delta

cucumbers_delta <- full_join(cucumbers_delta, sites, join_by("site_code"))
```

```{r}
ggplot(data = cucumbers_delta, aes(x = imp200m, y = delta_mass))+ geom_point()
```

# Arthropod Data

### Arthropod Abundance
Total number of arthropod observations by site and month
```{r}
arthropods_n <- arthropods %>%
    group_by(site_code,month)%>%
    summarise(n.obs = n())
arthropods_n
```

### Functional Groups
```{r}
#Functional groups across sites
arthropods_fun <- arthropods %>%
    group_by(fun_group, site_code,month)%>%
    summarise(n.obs = n())%>%
    mutate(fun_group = replace_na(fun_group, "Unknown"))
arthropods_fun 
unique(arthropods_fun$fun_group)
```

Functional Group Richness Analysis
```{r}
arthropods_wide <- arthropods_fun %>%
  mutate(site_month = paste(site_code, month, sep = "_"))%>%
    pivot_wider(
    names_from = site_month,
    values_from = n.obs,
    values_fill = 0  # fill missing combinations with 0
  )
```

## Final Datasets
Adding the abundance of each functional group, pollinator species richness, and functional group diversity to site dataset
```{r}
#Pollinator abundance by site by month
n.pol <- arthropods %>%
    filter(fun_group == "Pollinator")%>%
    group_by(month, site_code)%>%
    summarise(n.pol = n())

#Predator abundance by site by month
n.pred <- arthropods %>%
    filter(fun_group == "Predator" | fun_group == "Predator/Scavenger" | fun_group == "Parasitoid")%>%
    group_by(month, site_code)%>%
    summarise(n.pred = n())

#Herbivore abundance by site by month
n.herb <- n.pol <- arthropods %>%
    filter(fun_group == "Herbivore")%>%
    group_by(month, site_code)%>%
    summarise(n.herb = n())

#Detritivore abundance by site by month
n.det <- n.pol <- arthropods %>%
    filter(fun_group == "Detritivore")%>%
    group_by(month, site_code)%>%
    summarise(n.det = n())
```

Saving Data frames to Use in Analyses
```{r}
#Floral iNaturalist Data Wide format
write.csv(inat_wide, "/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/data/inat_wide.csv", row.names = FALSE)

#Site level data

#Arthropod data wide format

#Arthropod functional groups wide format
write.csv(arthropods_wide, "/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/data/arthropods_wide.csv", row.names = FALSE)
```



