---
title: "Data Cleaning"
output: html_document
date: "2025-08-29"
---

# Load Packages
```{r, message=FALSE}
library("tidyverse")
library("dplyr")
library("iNEXT")
library("sf")
library("units")
library("vegan")
```

# Read in the Data
```{r}
#Clear environment
rm(list = ls())

#Load in all datasets
setwd("/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research")
arthropods_jun_raw <- read.csv("data/Arthropod Data - June - Traps.csv", na.strings = c("", " "))
arthropods_jul_raw <- read.csv("data/Arthropod Data - July - Traps.csv", na.strings = c("", " "))
arthropods_aug_raw <- read.csv("data/Arthropod Data - August - Traps.csv", na.strings = c("", " "))
cucumbers_raw <- read.csv("data/cucumber_data.csv", na.strings = c("", " "))
sites_raw <- read.csv("data/DUG_data - fall_data.csv", na.strings = c("", " "))
inat_raw <- read.csv("data/observations-672273.csv", na.strings = c("", " "))

#Joining arthropod month datasets
arthropods <- rbind(arthropods_jun_raw, arthropods_jul_raw)
arthropods <-rbind(arthropods,arthropods_aug_raw)
```

# Explore the data
```{r}
#str(arthropods)
#str(cucumbers_raw)
#str(sites_raw)
```

# Data Cleaning 
Select subset of site variables
```{r}
#Select which site level variables you want to keep in dataframe
sites <- sites_raw %>%
    dplyr::select(Site, site_code, Area_m2, Plots, WealthIndex, tcc200m, imp200m, tcc500m,imp500m,CWD_m2,wood_m2,FWD_m2,logs,bareground_m2,floral_area_m2,dev_high500m, dev_low500m,	wetland500m, water500m,	dev_high1000m, dev_low1000m, water1000m, wetland1000m, shrub_grass1000m)
str(sites)
```

Descriptive statistics of site level variables
```{r}
site_statistics <- sites %>%
  summarise(across(c(Area_m2, Plots, WealthIndex, tcc200m, imp200m),
                   list(mean = ~mean(.x, na.rm = TRUE),
                        sd   = ~sd(.x, na.rm = TRUE)),
                   .names = "{.fn}_{.col}"))%>%
    pivot_longer(everything(),
               names_to = c("stat", "variable"),
               names_sep = "_") %>%
    pivot_wider(names_from = variable, values_from = value)
site_statistics 
```
Assign iNaturalist floral observations to sites
```{r}
#Convert iNaturalist data to an sf object
#Create buffer distances

#Convert gbif to sf points
sf_data <- st_as_sf(inat_raw, coords = c("longitude", "latitude"), crs = 4326)

#Convert cities.test to sf points
gardens.sf <- st_as_sf(sites_raw, coords = c("Long", "Lat"), crs = 4326)

#Create 45 km buffers around all cities
buffer_distance <- set_units(500, "m")  # 45 km in meters
gardens.buffer <- st_buffer(gardens.sf, dist = buffer_distance)
```

Assign all observations to a city
```{r}
# Perform spatial join: assign City to points within buffer
sf_data <- st_join(sf_data, gardens.buffer["site_code"], join = st_within)

# Fill points outside any city buffer
sf_data$site_code <- sf_data$site_code # Copy joined column

#Adding site codes for all chive (allium) observations manually since it was geo-obscured by iNat
manual_sites <- c(`81`="PAL", `183`="PAL", `202`="PAL", `637`="SLA", `649`="EDI",
                  `664`="EDI", `905`="EDI", `985`="SHO", `1005`="GW", `1012`="GW",
                  `1354`="RUB", `1356`="RUB", `1578`="SAM", `1640`="GABL",
                  `2101`="APP", `2202`="SLA", `2211`="SLA", `2214`="SLA",
                  `2446`="SHO", `2486`="CHA", `2511`="CHA")

sf_data$site_code[as.integer(names(manual_sites))] <- manual_sites


# Convert back to data frame if needed
inat_data <- as.data.frame(sf_data)

# Check unique city assignments
unique(inat_data$site_code)
```

Add floral observation abundance to site data
```{r}
## Group Summaries

# No. of observations
inat.obs.all <- inat_data %>%
  group_by(site_code) %>%
  summarise(floral.obs = n())

# Merge into site datasheet
sites <- sites %>%
  left_join(inat.obs.all, by = "site_code")
```

# Floral Biodiversity Metrics
### Extracting Biodiversity Values

* Summarize species counts per site
* Pivot dataframe wide to get into correct format for iNEXT
* Run iNEXT for estimated richness and diversity values
* Add values back to garden sites dataframe

```{r}
# Prepare iNaturalist data and convert to wide format
inat_wide <- inat_data %>%
  count(site_code,scientific_name) %>%
  pivot_wider(names_from = site_code, values_from = n, values_fill = 0)

# Prepare iNEXT input data
inat.iNEXTinput <- as.data.frame(inat_wide[,-1])

# Run iNEXT to find richness data
inat.iNEXT <- iNEXT(inat.iNEXTinput, q = 0, datatype = "abundance")

# Extract richness and diversity data
inat_richness <-  inat.iNEXT$AsyEst[inat.iNEXT$AsyEst$Diversity == "Species richness",]
inat_shannon <-  inat.iNEXT$AsyEst[inat.iNEXT$AsyEst$Diversity == "Shannon diversity",]
inat_simpson <-  inat.iNEXT$AsyEst[inat.iNEXT$AsyEst$Diversity == "Simpson diversity",]

# Match site_code to Assemblage
sites$flor.rich    <- inat_richness$Observed[match(sites$site_code, inat_richness$Assemblage)]
sites$flor.shannon <- inat_shannon$Observed[match(sites$site_code, inat_shannon$Assemblage)]
sites$flor.simpson <- inat_simpson$Observed[match(sites$site_code, inat_simpson$Assemblage)]
```

iNaturalist data summarized at the genus level for NMDS
```{r}
# Prepare iNaturalist data at the genus level
inat_wide <- inat_data %>%
  count(site_code,taxon_genus_name) %>%
  pivot_wider(names_from = taxon_genus_name, values_from = n, values_fill = 0)
```


# Bee Biodiversity Metrics
Total number of each bee species observed by site and month
```{r}
bees <- arthropods %>%
    filter(fam == "Apidae" |fam == "Halictidae"|fam == "Megachilidae"|fam == "Andrenidae"|fam == "Melittidae"| fam == "Colletidae")%>%
    mutate(specie = tidyr::replace_na(specie, "spp."),
        spec_ID = paste(genus,specie, sep = " "))%>%
    group_by(spec_ID, site_code, month)%>%
    summarise(spec.obs = n())
```

Bee Diversity Analysis
```{r}
bees_wide <- bees %>%
  mutate(site_month = paste(site_code, month, sep = "_"))%>%
    pivot_wider(
    id_cols = site_month,
    names_from = spec_ID,
    values_from = spec.obs,
    values_fill = 0  # fill missing combinations with 0
  )
```


# Cucumber Data
```{r}
#Average cucumber values by treatment by site
cucumbers_avg <- cucumbers_raw %>%
    mutate(seed_mass_ratio = no_seeds/mass_g)%>%
    group_by(site_code, treatment) %>%
    summarise(
        avg_mass = mean(mass_g, na.rm = TRUE),
        avg_seeds = mean(no_seeds, na.rm = TRUE),
        avg_length = mean(length_mm, na.rm = TRUE),
        avg_width = mean(width, na.rm = TRUE),
        avg_volume = mean(volume_mL, na.rm = TRUE),
        prop_cylindrical = mean(cylindrical == "Yes", na.rm = TRUE),
        avg_seed_mass_ratio = mean(seed_mass_ratio, na.rm = TRUE),
        n_cucumbers = n(),.groups = "drop")%>%
        complete(
    site_code = c(unique(cucumbers_raw$site_code), "JEF"),
    treatment,
    fill = list(n_cucumbers = 0))
cucumbers_avg
 
#Difference (Pollinated - Control) for cucumber values by site
cucumbers_delta <-  cucumbers_avg %>%
   arrange(site_code, treatment) %>% 
    group_by(site_code) %>%
  summarise(
    delta_mass  = diff(avg_mass),
    delta_seeds = diff(avg_seeds),
    delta_length = diff(avg_length),
    delta_width = diff(avg_width),
    delta_volume = diff(avg_volume),
    delta_cylindrical = diff(prop_cylindrical),
    delta_seed_mass_ratio = diff(avg_seed_mass_ratio),
    delta_no = diff(n_cucumbers))
cucumbers_delta

cucumbers_avg <- full_join(cucumbers_avg, sites, join_by("site_code"))
```

# Arthropod Data

### Arthropod Abundance
Total number of arthropod observations by site and month
```{r}
arthropods_n <- arthropods %>%
    group_by(site_code,month)%>%
    summarise(n.obs = n())
arthropods_n
```

### Functional Groups
```{r}
#Total arthropods each functional group (manuscript)
arthropods_fun_total <- arthropods %>%
    group_by(fun_group)%>%
    summarise(n.obs = n())

#Functional groups across sites
arthropods_fun <- arthropods %>%
    group_by(fun_group, site_code,month)%>%
    summarise(n.obs = n())%>%
    mutate(fun_group = replace_na(fun_group, "Unknown"))
arthropods_fun 
unique(arthropods_fun$fun_group)
```

Functional Group Richness Analysis
```{r}
arthropods_wide <- arthropods_fun %>%
  mutate(site_month = paste(site_code, month, sep = "_")) %>%
  pivot_wider(
    id_cols = site_month,
    names_from = fun_group,
    values_from = n.obs,
    values_fill = 0
  )
```

## Final Datasets
Adding the abundance of each functional group, pollinator species richness, and functional group diversity to site dataset
```{r}
sites_final <- arthropods %>%
  mutate(
    fun_group = case_when(
      fun_group == "Pollinator" ~ "pol",
      fun_group %in% c("Predator", "Predator/Scavenger", "Parasitoid") ~ "pred",
      fun_group == "Herbivore" ~ "herb",
      fun_group == "Detritivore" ~ "det"
    )
  ) %>%
  group_by(site_code, month, fun_group) %>%
  summarise(n = n(), .groups = "drop") %>%
  tidyr::pivot_wider(
    names_from = fun_group,
    values_from = n,
    names_prefix = "n.",
    values_fill = 0
  ) %>%
  left_join(sites, by = "site_code") %>%
  left_join(cucumbers_delta, by = "site_code")
```

#Saving Data frames
```{r}
#Floral iNaturalist Data Wide format
write.csv(inat_wide, "/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/data/inat_wide.csv", row.names = FALSE)

#Site level data
write.csv(sites_final, "/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/data/sites_all.csv", row.names = FALSE)

#Cucumber averages data
write.csv(cucumbers_avg, "/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/data/cucumbers_avg.csv", row.names = FALSE)

#Bee data wide format
write.csv(bees_wide, "/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/data/bees_wide.csv", row.names = FALSE)

#Arthropod functional groups wide format
write.csv(arthropods_wide, "/Users/aska1693/Downloads/Chapter3_DUGresearch/dug-research/data/arthropods_wide.csv", row.names = FALSE)
```



