---
title: "Data Cleaning"
output: html_document
date: "2025-08-29"
---

# Load Packages
```{r, message=FALSE}
library("tidyverse")
library("dplyr")
library("iNEXT")
library("sf")
library("units")
library("vegan")
```

# Read in the Data
```{r}
#Clear environment
rm(list = ls())

#Load in all datasets
arthropods_jun_raw <- read.csv("../data/Arthropod Data - June - Traps.csv", na.strings = c("", " "))
arthropods_jul_raw <- read.csv("../data/Arthropod Data - July - Traps.csv", na.strings = c("", " "))
arthropods_aug_raw <- read.csv("../data/Arthropod Data - August - Traps.csv", na.strings = c("", " "))
cucumbers_raw <- read.csv("../data/cucumber_data.csv", na.strings = c("", " "))
sites_raw <- read.csv("../data/DUG_sites.csv", na.strings = c("", " "))
inat_raw <- read.csv("../data/observations-672273.csv", na.strings = c("", " "))

#Joining arthropod month datasets
arthropods <- rbind(arthropods_jun_raw, arthropods_jul_raw)
arthropods <-rbind(arthropods,arthropods_aug_raw)
```

# Explore the data
```{r}
#str(arthropods)
#str(cucumbers_raw)
#str(sites_raw)
```

# Data Cleaning 
Select subset of site variables
```{r}
#Select which site level variables you want to keep in dataframe
sites <- sites_raw %>%
    dplyr::select(Site, site_code, Area_m2, Plots, Lat, Long, estYear, WealthIndex,PovertyIndex, DiversityIndex, MedNetWorth, MedHomeVal, VacantHU, RenterHU, tcc_200m, imp_200m, tcc_500m, imp_500m, CWD_m2, wood_m2, FWD_m2,logs, bareground_m2,floral_area_m2,dev_high_500m, dev_low_500m,wetland_500m, water_500m,dev_high_1000m, dev_low_1000m, water_1000m, wetland_1000m, shrub_grass_1000m, gbif.rich, gbif.shannon,gbif.simpson)
str(sites)
```

Descriptive statistics of site level variables
```{r}
site_statistics <- sites %>%
  summarise(across(c(Area_m2, Plots, WealthIndex, tcc_200m, imp_200m),
                   list(mean = ~mean(.x, na.rm = TRUE),
                        sd   = ~sd(.x, na.rm = TRUE)),
                   .names = "{.fn}_{.col}"))%>%
    pivot_longer(everything(),
               names_to = c("stat", "variable"),
               names_sep = "_") %>%
    pivot_wider(names_from = variable, values_from = value)
site_statistics 
```

## Garden Floral Biodiversity

Spatial Geometry and Buffers
```{r}
# Convert raw coordinates to standard WGS84 spatial points
sf_data_wgs84  <- st_as_sf(inat_raw, coords = c("longitude", "latitude"), crs = 4326)
gardens.sf_wgs84 <- st_as_sf(sites, coords = c("Long", "Lat"), crs = 4326)

# Transform coordinate systems to a metric projection (UTM or Albers) 
# so st_buffer uses true meters
# (Using EPSG:5070 - NAD83 Albers Conical Equal Area as an effective standard standard)
sf_data  <- st_transform(sf_data_wgs84, crs = 5070)
gardens.sf <- st_transform(gardens.sf_wgs84, crs = 5070)

# Create 500 m buffer around gardens to catch all datapoints associated with our project
buffer_distance <- set_units(500, "m") 
gardens.buffer  <- st_buffer(gardens.sf, dist = buffer_distance)
```

Spatial join
```{r}
# Assign observations to gardens based on spatial boundaries
sf_data <- st_join(sf_data, gardens.buffer["site_code"], join = st_within)

# Create your manual mapping vector
manual_sites <- c(`81`="PAL", `183`="PAL", `202`="PAL", `637`="SLA", `649`="EDI",
                  `664`="EDI", `905`="EDI", `985`="SHO", `1005`="GW", `1012`="GW",
                  `1354`="RUB", `1356`="RUB", `1578`="SAM", `1640`="GABL",
                  `2101`="APP", `2202`="SLA", `2211`="SLA", `2214`="SLA",
                  `2446`="SHO", `2486`="CHA", `2511`="CHA")

# Process spatial vectors into a structured dataframe
inat_data <- sf_data %>% 
  st_drop_geometry() %>%
  mutate(row_id = as.character(row_number())) %>% 
  mutate(site_code = case_when(
    row_id %in% names(manual_sites) ~ manual_sites[row_id],
    TRUE ~ site_code
  )) %>% 
  select(-row_id) %>% 
  filter(!is.na(site_code))
```

Extract Floral Biodiversity Metrics
```{r}
inat_wide <- inat_data %>%
  count(site_code,scientific_name) %>%
  filter(!is.na(scientific_name)) %>% # Protects against empty species classifications
  pivot_wider(names_from = site_code, values_from = n, values_fill = 0)

# Convert matrix column to actual data frame rownames so iNEXT reads site metadata correctly
inat.iNEXTinput <- inat_wide %>% 
  column_to_rownames(var = "scientific_name") %>% 
  as.data.frame()

# Run iNEXT to get richness and diversity estimates
inat.iNEXT <- iNEXT(inat.iNEXTinput, q = 0, datatype = "abundance")

# Extract richness indices
inat_richness <- inat.iNEXT$AsyEst[inat.iNEXT$AsyEst$Diversity == "Species richness", ]
inat_shannon  <- inat.iNEXT$AsyEst[inat.iNEXT$AsyEst$Diversity == "Shannon diversity", ]
inat_simpson  <- inat.iNEXT$AsyEst[inat.iNEXT$AsyEst$Diversity == "Simpson diversity", ]

# Merge metrics cleanly back to site rows
#Ued observed not estimated, since we sampled every plant at each site
sites$inat.rich    <- inat_richness$Observed[match(sites$site_code, inat_richness$Assemblage)]
sites$inat.shannon <- inat_shannon$Observed[match(sites$site_code, inat_shannon$Assemblage)]
sites$inat.simpson <- inat_simpson$Observed[match(sites$site_code, inat_simpson$Assemblage)]
```

Add floral observation abundance to site data
```{r}
sites <- inat_data %>%
  group_by(site_code) %>%
  summarise(floral.obs = n()) %>%
  left_join(sites, ., by = "site_code")
```

iNaturalist data summarized at the family level for NMDS
```{r}
# Prepare iNaturalist data at the genus level
inat_wide <- inat_data %>%
  count(site_code,taxon_family_name) %>%
  pivot_wider(names_from = taxon_family_name, values_from = n, values_fill = 0) %>%
  column_to_rownames(var = "site_code")
```


# Bee Biodiversity Metrics
```{r}
#Total number of each bee species observed by site and month
bees <- arthropods %>%
    filter(fam == "Apidae" |fam == "Halictidae"|fam == "Megachilidae"|fam == "Andrenidae"|fam == "Melittidae"| fam == "Colletidae")%>%
    mutate(specie = tidyr::replace_na(specie, "spp."),
        spec_ID = paste(genus,specie, sep = " "))%>%
    group_by(spec_ID, site_code, month)%>%
    summarise(spec.obs = n())

#Total number of each bee species observed by site across full summer
bees_agg <- arthropods %>%
    filter(fam == "Apidae" |fam == "Halictidae"|fam == "Megachilidae"|fam == "Andrenidae"|fam == "Melittidae"| fam == "Colletidae")%>%
    mutate(specie = tidyr::replace_na(specie, "spp."),
        spec_ID = paste(genus,specie, sep = " "))%>%
    group_by(spec_ID, site_code)%>%
    summarise(spec.obs = n())
```


Bee Diversity Analysis
```{r}
bees_wide <- bees %>%
mutate(site_month = paste(site_code, month, sep = "_")) %>%
  ungroup() %>%
  pivot_wider(
    id_cols = spec_ID,
    names_from = site_month,
    values_from = spec.obs,
    values_fill = list(spec.obs = 0)
  ) %>%
  column_to_rownames(var = "spec_ID")

# Run iNEXT to find richness data
bees.iNEXT <- iNEXT(bees_wide, q = 0, datatype = "abundance")

# Extract richness and diversity data
inext_cleaned <- bees.iNEXT$AsyEst %>%
select(Assemblage, Diversity, Estimator, Observed) %>%
  mutate(
    Estimator = if_else(Estimator == Inf, Observed, Estimator),
    Diversity = case_when(
      Diversity == "Species richness"   ~ "bee.rich",
      Diversity == "Shannon diversity"  ~ "bee.shannon",
      Diversity == "Simpson diversity"  ~ "bee.simpson",
      TRUE ~ Diversity)) %>%
  select(-Estimator) %>%
  pivot_wider(
    names_from = Diversity,
    values_from = Observed)%>%
    separate_wider_delim(
    cols = Assemblage,
    delim = "_",
    names = c("site_code", "month")
  )
```


# Cucumber Data
```{r}
#Average cucumber values by treatment by site
cucumbers_avg <- cucumbers_raw %>%
    mutate(seed_mass_ratio = no_seeds/mass_g)%>%
    group_by(site_code, treatment) %>%
    summarise(
        avg_mass = mean(mass_g, na.rm = TRUE),
        avg_seeds = mean(no_seeds, na.rm = TRUE),
        avg_length = mean(length_mm, na.rm = TRUE),
        avg_width = mean(width, na.rm = TRUE),
        avg_volume = mean(volume_mL, na.rm = TRUE),
        prop_cylindrical = mean(cylindrical == "Yes", na.rm = TRUE),
        avg_seed_mass_ratio = mean(seed_mass_ratio, na.rm = TRUE),
        n_cucumbers = n(),.groups = "drop")%>%
        complete(
    site_code = c(unique(cucumbers_raw$site_code), "JEF"),
    treatment,
    fill = list(n_cucumbers = 0))
cucumbers_avg
 
#Difference (Control - Pollinated) for cucumber values by site
cucumbers_delta <- cucumbers_avg %>%
  group_by(site_code) %>%
  summarise(
    delta_mass  = avg_mass[treatment == "Control"] - avg_mass[treatment == "Pollinated"],
    delta_seeds = avg_seeds[treatment == "Control"] - avg_seeds[treatment == "Pollinated"],
    delta_length = avg_length[treatment == "Control"] - avg_length[treatment == "Pollinated"],
    delta_width = avg_width[treatment == "Control"] - avg_width[treatment == "Pollinated"],
    delta_volume = avg_volume[treatment == "Control"] - avg_volume[treatment == "Pollinated"],
    delta_cylindrical = prop_cylindrical[treatment == "Control"] - prop_cylindrical[treatment == "Pollinated"],
    delta_seed_mass_ratio = avg_seed_mass_ratio[treatment == "Control"] - avg_seed_mass_ratio[treatment == "Pollinated"],
    delta_no = n_cucumbers[treatment == "Control"] - n_cucumbers[treatment == "Pollinated"]
  )
cucumbers_avg <- full_join(cucumbers_avg, sites, join_by("site_code"))
```

# Arthropod Data

### Arthropod Abundance
Total number of arthropod observations by site and month
```{r}
arthropods_n <- arthropods %>%
    group_by(site_code,month)%>%
    summarise(n.obs = n())
arthropods_n
```

### Functional Groups
```{r}
#Total arthropods each functional group (manuscript)
arthropods_fun_total <- arthropods %>%
    group_by(fun_group)%>%
    summarise(n.obs = n())

#Functional groups across sites
arthropods_fun <- arthropods %>%
    group_by(fun_group, site_code,month)%>%
    summarise(n.obs = n())%>%
    mutate(fun_group = replace_na(fun_group, "Unknown"))
arthropods_fun 
unique(arthropods_fun$fun_group)
```

Functional Group Richness Analysis
```{r}
arthropods_wide_sum <- arthropods %>%
  # Filter out missing functional groups so they don't warp community distances
  filter(!is.na(fun_group) & fun_group != "Unknown") %>%
  group_by(site_code, fun_group) %>%
  summarise(n.obs = n(), .groups = "drop") %>%
  pivot_wider(
    id_cols = site_code,
    names_from = fun_group,
    values_from = n.obs,
    values_fill = 0) %>%
    #Isolate site identifiers out of the numerical data matrix
  column_to_rownames(var = "site_code")

arthropods_wide <- arthropods %>%
  filter(!is.na(fun_group) & fun_group != "Unknown") %>% # Filter out missing functional groups
  mutate(site_month = paste(site_code, month, sep = "_")) %>%
  group_by(site_month, fun_group) %>%
  summarise(n.obs = n(), .groups = "drop") %>%
  pivot_wider(
    id_cols = site_month,
    names_from = fun_group,
    values_from = n.obs,
    values_fill = 0) %>%
  column_to_rownames(var = "site_month")
```

## Final Datasets
Adding the abundance of each functional group, pollinator species richness, and functional group diversity to site dataset
```{r}
sites_final <- arthropods %>%
  mutate(
    fun_group = case_when(
      fun_group == "Pollinator" ~ "pol",
      fun_group %in% c("Predator", "Predator/Scavenger", "Parasitoid","Parasite","Kleptoparasite") ~ "pred",
      fun_group == "Herbivore" ~ "herb",
      fun_group == "Detritivore" ~ "det",
      fun_group == "Omnivore" ~ "omn"
    )
  ) %>%
  group_by(site_code, month, fun_group) %>%
  summarise(n = n(), .groups = "drop") %>%
  tidyr::pivot_wider(
    names_from = fun_group,
    values_from = n,
    names_prefix = "n.",
    values_fill = 0
  ) %>%
  left_join(sites, by = "site_code") %>%
  left_join(cucumbers_delta, by = "site_code")%>%
    left_join(arthropods_n, by = c("site_code","month"))


# Join the site-level iNEXT data back into the monthly dataframe
sites_final <- sites_final %>%
  left_join(inext_cleaned, by = c("site_code","month"))
```

#Save Output Dataframes
```{r}
#Site level data
write.csv(sites_final, "../data/sites_all.csv", row.names = FALSE)
#Cucumber averages data
write.csv(cucumbers_avg, "../data/cucumbers_avg.csv", row.names = FALSE)

#----------------------------------------
## Wide datasets for Community Analyses
#Floral iNaturalist Data Wide format
write.csv(inat_wide, "../data/NMDS_datasets/inat_wide.csv", row.names = TRUE)

#Bee data
write.csv(bees, "../data/NMDS_datasets/bees.csv", row.names = TRUE)
write.csv(bees_agg, "../data/NMDS_datasets/bees_agg.csv", row.names = TRUE)

#Arthropod functional groups wide format
write.csv(arthropods_wide, "../data/NMDS_datasets/arthropods_wide.csv", row.names = TRUE)
write.csv(arthropods_wide_sum, "../data/NMDS_datasets/arthropods_wide_sum.csv", row.names = TRUE)
```

# Session Info and Packages
```{r}
packageVersion("iNEXT")
```

